### 2015-04-05 Introduction_trying.tex
added old tex for reference

\documentclass{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{epstopdf}
\usepackage{float}

\title{Toeplitz Matrices, Szeg\"{o} Limit Theorem}
\author{Tyler Friedman}

\newtheorem{mydef}{Definition}[section]
\newtheorem{theorem}{Theorem}[section]
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{claim}[theorem]{Claim}

\newtheorem{exmp}{Example}[section]

\begin{document}
\maketitle

\section{Introduction}

Suppose $f(x,p)$ :   $\mathbb{R}^{2}  \rightarrow \mathbb{R}$ is a real-valued function defined on the cylinder s.t. $-\pi \le x \le \pi,  0 \le p \le 1$.  We can then define the Fourier series of such a function:
\begin{equation}
f(x,p) = \displaystyle\sum\limits_{k=-\infty}^\infty f_{k}(p)e^{ikx} \label{fourier}
\end{equation}
Suppose we then arrange the coefficients of this Fourier series, the $f_{k}(p)$, into a $Toeplitz$ matrix.

\begin{mydef}
A Toeplitz matrix is an $n\times n$ matrix of the form 
\[
A = 
\begin{pmatrix}
a_{0} & a_{1} & a_{2} & \cdots & \cdots & a_{n-1} \\
a_{-1} & a_{0} & a_{1} & \ddots &  & \vdots \\
a_{-2} & a_{-1} & \ddots & \ddots & \ddots & \vdots \\
\vdots & \ddots & \ddots & \ddots & a_{1} & a_{2} \\
\vdots &  & \ddots & a_{-1} & a_{0} & a_{1} \\
a_{-n+1} & \cdots & \cdots & a_{-2} & a_{-1} & a_{0}
\end{pmatrix}
\]
where $a_{i,j} = a_{i+1,j+1}, 1 \le i,j \le n$
\end{mydef}

\section{Weyl Quantization}
In particular, suppose we form a variant of the Toeplitz matrix, the Szeg\"{o} -Toeplitz matrix, $T_{f,N}$, $N \ge 1$, where
\begin{equation}
t_{i,j} = f_{j-i}(\frac{1}{2}\ \frac{i+j}{N+1}), 1 \le i,j \le N+1 \label{szegomap}
\end{equation}

The eigenvalues of such a matrix is an area of considerable interest.  For example. consider the normalized function $f(x,p) = (\cos(x) + p\sin(x))/\sqrt{2}$ with domain defined as above. The specturm of $T_{f,N}$, as N varies from $1$ to $\infty$ gives us the following graph:

\begin{figure} [H]
\centerline{\includegraphics{cosx+psinx}}
\caption{Distribution of eigenvalues}
\end{figure}

Notice how the eigenvalues become more concentrated around $\pm0.7$ as $N \rightarrow \infty$.  Our goal is to find some function that describes the distribution of these eigenvalues, and can explain why they become so densely populated at certain points. With this is in mind, we begin by utilitzing the Szeg\"{o}-Limit Theorem.

\begin{theorem} \emph{(Szeg\"{o}-Limit Theorem)} \label{Szego} If f is not horrible, then $\forall k \ge 1, k \in \mathbb{Z}$: \begin{equation}
\lim_{N \to \infty} \frac{1}{N+1} Tr((T_{f,N})^k) = \frac{1}{2\pi} \int^{\pi}_{-\pi} \! \int^1_0  f_{f,N}(x,p)^k \,dp \,dx \label{szego}
\end{equation} 
\end{theorem}

 Because $T_{f,N}$ is Hermitian, it can be diagonlized.  Using this property, along with the fact that $Tr(AB) = Tr(BA)$, it is not difficult to rewrite Equation \ref{szego} as

\begin{equation} 
\lim_{N \to \infty} \frac{1}{N+1} \displaystyle\sum\limits_{j=0}^{N} (\lambda_{j}^{(N)})^k= \frac{1}{2\pi} \int^{\pi}_{-\pi} \! \int^1_0  f_{f,N}(x,p)^k \,dp \,dx 
\end{equation} Further, it can be shown that this slightly altered form of the Szeg\"{o}-Limit Theorem is in fact just one instance of a more powerful equality.  In general:

\begin{corollary}
If $\varphi \ cont:[-1,1] \rightarrow \mathbb{R}$, then
\begin{equation}
\lim_{N \to \infty} \frac{1}{N+1}  \displaystyle\sum\limits_{j=0}^N \varphi(\lambda_{j}^{(N)})= \frac{1}{2\pi} \int^{\pi}_{-\pi} \! \int^1_0  \varphi(f_{f,N}(x,p)) \,dp \,dx \label{BIGGUY}
\end{equation}
\end{corollary}

Consider the left side of this equation to be in the form of a Riemman sum. If the $\lambda_{j}^{(N)}$ were evenly distributed, we would be able to rewrite this equation as

\begin{equation} 
\int^1_{-1} \varphi(t) \,dt 
\end{equation} Yet, from Figure 1 we can tell that this is not the case; consequently, we must compensate for this unequal distribution with some correction function, $\beta(t)$ s.t.

\begin{equation}
\lim_{N \to \infty} \frac{1}{N+1}  \displaystyle\sum\limits_{j=0}^N \varphi(\lambda_{j}^{(N)}) = \int^1_{-1} \varphi(t) \beta (t) \,dt \label{HOW}
\end{equation} This function, $\beta(t)$, is exactly the function that will describe the distribution of our eigenvalues. WHY? NEED EXPLANATION.  Combining Equations \ref{BIGGUY} and \ref{HOW} we get

\begin{equation} 
\int^{\pi}_{-\pi} \! \int^1_0  \varphi(f_{f,N}(x,p)) \,dp \,dx = \int^1_{-1} \varphi(t) \beta (t) \,dt \label{beta} 
\end{equation}

To solve for $\beta(x)$  using exact methods, we can consider using the Coarea formula.

\begin{theorem}
\emph{(Coarea formula)} \label{coarea}
Suppose that $\Omega$ is an open set in $\mathbb{R}^{n}$, and f is a real-valued Lipshitz function on $\Omega$.  Then, for an $L^{1}$ function $\Psi$,
\begin{equation}
\iint\limits_\Omega \Psi(x)\lvert\nabla f(x)\rvert \,dx =  \int_{Im(f)} \! (\int_{f^{-1}(x)} \Psi \,ds) \,dx
\end{equation}
\end{theorem}

For our purposes, we can let

\begin{equation} 
\Psi = \frac{\varphi(f(x,p))}{\lvert\nabla f(x,p)\rvert} 
\end{equation} and

\begin{equation} 
\Omega = [-\pi,\pi] \times [0,1] 
\end{equation} We can then rewrite the left side of Equation \ref{beta} as 
\begin{equation} \begin{split} 
\int^{\pi}_{-\pi} \! \int^1_0  \varphi(f_{f,N}(x,p)) \,dp \,dx& =  \iint\limits_\Omega \Psi\lvert\nabla f \rvert\, dp \, dx  \\ 
& = \int_{Im(f)} \! \left(\int_{f^{-1}(t)} \frac{\varphi(f(x,p))}{\lvert\nabla f(x,p)\rvert} \,ds\right) \,dt    \text{ $...$ by the Coarea fomula} \\
& = \int_{Im(f)} \! \left(\int_{f^{-1}(t)} \frac{\varphi(t)}{\lvert\nabla f(x,p)\rvert} \,ds\right) \,dt\\ & = \int_{Im(f)} \varphi(t) \! \left(\int_{f^{-1}(t)} \frac{1}{\lvert\nabla f(x,p)\rvert} \,ds\right) \,dt \end{split} 
\end{equation} Notice that the inner integral is exactly the $\beta(x)$ that we originally set out to find:

\begin{equation}
\beta(x) = \int_{f^{-1}(t)} \frac{1}{\lvert\nabla f(x,p)\rvert} \,ds
\end{equation}

With that said, we know of no reasonable method to analytically compute such an integral. Thus instead we focus our attention on approximating this unknown distribution function.  Our method of choice is orthogonal polynomials, specifically the normalized $Legendre$ polynomial. It is important to note that  these polynomials are only orthogonal on the interval $[-1,1]$, and thus that is the only interval on which our approximation will  make sense.

Let 
\begin{equation} 
\beta (x) = \displaystyle\sum\limits_{n=0}^N a_n P_n(x) 
\end{equation} where

\begin{equation} 
a_n = \int^1_{-1} \beta (x) P_n(x) \, dx,\  P_n = \lvert\lvert{p_n}\rvert\rvert 
\end{equation} and the unnormalized Legendre polynomials, $p_n$, are

\begin{equation} 
1, x, \frac{1}{2}(3x^2 - 1), \frac{1}{2}(5x^3 -3x), \frac{1}{8}(35x^4 - 30x^2 + 3), \cdots 
\end{equation} Using the equality from Equation \ref{beta}, we can rewrite $a_n$ as

\begin{equation} 
a_n = \int^{\pi}_{-\pi} \! \int^1_0  P_n(f_{f,N}(x,p)) \,dp \,dx
\end{equation} Using this approximation, we find the graph of $\beta (x)$ from our initial example to be

\begin{figure} [H] 
\centerline{\includegraphics[scale=.50]{legendre_apprx2}} 
\caption{Distribution approximation function} 
\end{figure} Notice the two peaks around $\pm0.7$.  This is consistent with our data from Figure 1, in which the eigenvalues are most densely distributed at those two numbers.

Another interesting case to consider is where the Szeg\"{o}-Toeplitz matrix formed has non-zero values everywhere, as opposed to the previous example where only two diagonals contained such values.  Let $$f(x,p) = xp, [-\pi,\pi]\times[0,1]$$ \begin{figure} [H] \centerline{\includegraphics[scale=.60]{eigenvalues_xp}} \caption{eigenvalues for given N} \end{figure} \clearpage \begin{figure} [H] \centerline{\includegraphics[scale=.50]{legendre_apprx_xp}} \caption{Distribution approximation function} \end{figure}  Once again we find that the peak of our distribution approximation function corresponds exactly to the area of highest concentration among eigenvalues in the spectrum.

We have just provided

\section{Berezin-Toeplitz Quantization}

While very interesting, the Weyl quantization method applies only to real-valued functions, and the true focus of this research is understanding the distributions of much more interesting functions. We are consequently motivated to define a different quantization method, the Berezin-Toeplitz Quantization, which will allow us to explore more interesting cases. To do so, we begin by considering the domain $(x,p)\in [0,2\pi]\times\mathbb{R}$, and imposing a complex variable z s.t. $z = x-ip \in \mathbb{C}$. We can then form a geometric quantization to the Bergmann Space, $\mathcal{B}$, of the cylinder where $\mathcal{B} = \Psi(z)$, defined s.t.
\begin{enumerate}
\item $\Psi$ is analytic, i.e. $\Psi$ is not a function of $\overline{z}$
\item $\Psi$ is periodic in $z$, i.e. $\Psi(z + 2\pi) = \Psi(z)$
\item $\lvert\lvert\Psi\rvert\rvert^2 =  \int^{2\pi}_{0} \! \int^{\infty}_{-\infty}  \lvert\Psi(z)\rvert^{2}e^{-Np^{2}} \,dp \,dx< \infty, N=\frac{1}{\hbar}$
\end{enumerate}

We define the Hermitian inner product on $\mathcal{B}$ s.t.

$$ \forall \Psi_{1},\Psi_{2} \in \mathcal{B}, \langle\Psi_{1},\Psi_{2}\rangle = \int^{2\pi}_{0} \! \int^{\infty}_{-\infty}  \Psi_{1}(z)\overline{\Psi_{2}(z)}e^{-Np^{2}} \,dp \,dx$$

Our goal is now to find an orthonormal basis of $\mathcal{B}$, which we can use to define the Berezin-Toeplitz operator. \begin{proposition} $\forall n \in\mathbb{Z}, e^{inz}\in\mathcal{B}$ \end{proposition} We see how this is true because this generalized vector fulfills the three conditions we just set out for $\mathcal{B}$ :

\begin{enumerate}
\item 
$e^{inz} = \displaystyle\sum\limits_{k=0}^\infty \frac{1}{k!}(inz)^k$ by Taylor's theorem.  There are clearly no $\overline{z}$.

\item
\begin{equation*}
\begin{split}
e^{in(z+2\pi)} &= e^{inz} e^{in2\pi} \\
& = e^{inz}\cdot 1 \\
& = e^{inz}
\end{split}
\end{equation*}

\item 
It can be shown through fairly straightforward calculation that 
\begin{equation}
\lvert\lvert e^{inz}\rvert\rvert^2 = \frac{2\pi^{3/2}}{N^{\frac{1}{4}}}e^{\frac{\pi^2}{2N}} < \infty \label{normalizer}
\end{equation}
\end{enumerate} Since we are looking for an orthonormal basis, we divide by the length of $e^{inz}$ found in Equation \ref{normalizer}.

\begin{mydef}
$\forall n \in \mathbb{Z}, e_{n}(z) := \frac{e^{inz}}{\sqrt{T}}, T = \frac{2\pi^{3/2}}{N^{\frac{1}{4}}}e^{\frac{\pi^2}{2N}}$
\end{mydef} From our definition of $e_n(z)$, it follows shortly thereafter that  $\langle e^{inz},e^{imz}\rangle = \delta_{nm}$, and consequently we can claim that $\{e_n | n\in \mathbb{Z}\}$ is an orthonormal basis of $\mathcal{B}$.

Let $\mathcal{H} = span\{e_n |\, 0\le n \le N\}$.  Then take $f: [0,2\pi]\times\mathbb{R} \rightarrow\mathbb{R}$, and we are now able to define the Berezin-Toeplitz Operator of $f$

\begin{mydef}
\emph{(Berezin-Toeplitz Operator)}
$Op(f):\Psi \rightarrow f\Psi\rightarrow\Pi(f\Psi)$, where $\Pi$ is the othogonal projection of $\Psi$  onto $\mathcal{B}$
\end{mydef}

In other words, the operator takes an element of $\mathcal{B}$ and hits it with $f$, but because $f\Psi\notin\mathcal{B}$ (consider $f(x,p) = cosx + psinx$), we must then project back onto the Bergmann space, hence the orthogonal projection.

We can rewrite

\begin{equation}
\Pi(f\Psi) = \displaystyle\sum\limits_{n=0}^N\langle f\Psi,e_n\rangle e_n
\end{equation}

We now want to find the matrix of $Op(f)$ $w.r.t$ $\{e_n| n=0,1,2,\cdots,N\}$

\begin{equation}
\begin{split}
t_{m,n} &= \langle Op(f)(e_n),e_m\rangle \\
& =\langle fe_n,e_m\rangle \text{$\cdots$ because $\Pi$ is adjoint} \\
& = \frac{\sqrt{N}}{2\pi^{\frac{3}{2}}}e^{-\frac{n^2+m^2}{2N}}  \int^{2\pi}_{0} \! \int^{\infty}_{-\infty}f(x,p)e^{in(x-ip)}\overline{e^{im(x-ip)}}e^{-Np^{2}} \,dp \,dx \\
& =  \frac{\sqrt{N}}{2\pi^{\frac{3}{2}}}e^{-\frac{n^2+m^2}{2N}}  \int^{2\pi}_{0} \! \int^{\infty}_{-\infty}f(x,p)e^{i(n-m)x}e^{(n+m)p-Np^{2}} \,dp \,dx
\end{split}
\end{equation}

Recall that $\mathcal{H} = span\{e_n, 0\le n \le N\}$.  If we rewrite the range of $n$ as $0\le \frac{n}{N} \le 1$, then $\mathcal{H}$ can be thought of as the span\{eigenvectors of Op(p) with eigenvalues in $[0,1]$\}.  Hence we can rewrite the quantization as

\begin{equation}
\frac{\sqrt{N}}{2\pi^{\frac{3}{2}}}e^{-\frac{n^2+m^2}{2N}}  \int^{2\pi}_{0} \! \int^{1}_{0}f(x,p)e^{i(n-m)x}e^{(n+m)p-Np^{2}} \,dp \,dx
\end{equation} using the corresponding classical region as was used with the Weyl Quantization.  This final result is the Berezin-Toeplitz quantization we originally set out to find.  Notice that to this point we have made no assumptions about $f$ being real valued.

\section{Dirac Delta Function}

For simplicity, let
$$A_{m,n}^N = \frac{\sqrt{N}}{2\pi^{\frac{3}{2}}}e^{-\frac{n^2+m^2}{2N}}$$ Using the Berezin-Toeplitz Quanitzation, we are now able to to consider the spectrum of more interesting functions.  The most elementary such function we can consider is the Dirac Delta Function.  For this generalized function, we find its matrix to be

\begin{equation} 
\begin{split} 
t_{m,n} &=  A_{m,n}^N\int^{2\pi}_{0} \! \int^{1}_{0}\delta(x_{0},p_{0})e^{i(n-m)x}e^{(n+m)p-Np^{2}} \,dp \,dx \\ 
&=A_{m,n}^Ne^{i(n-m)x_{0}}e^{(n+m)p_{0}-Np_{0}^{2}} 
\end{split} 
\end{equation} For $x_{0} = 1, p_{0} = 1/3$, we get

\begin{figure} [H]\centerline{\includegraphics[scale=.62]{eigenvalues_delta}} \caption{Spectrum of the Dirac Delta Function} \end{figure} From the graph we conclude that the delta function is a linear projector (?) times a linearly increasing constant in the context of the B-T quantization.

Motivated by finding a more interesting case, we now study the more slightly more complicated Dirac Delta Function associated with a Curve.

\begin{mydef} The Dirac Delta Function associated with a Curve, $\delta_{\gamma}$, is the generalized function s.t. $\forall\ \varphi: [0,2\pi] \times \mathbb{R} \rightarrow \mathbb{R}$ "nice", $$  \int^{2\pi}_{0} \! \int^{1}_{0}\delta_{\gamma}(x,p)\varphi(x,p) \,dp \,dx \\ = \int_{\gamma} \varphi \,ds$$ 
\end{mydef} The simplest curve to consider for our domain is the ellipse

\begin{equation} 
\left(\frac{x}{2\pi}\right)^2 + p^2  = 1, \nonumber 
\end{equation} where $0\le x\le\frac{\pi}{2}, 0\le p \le 1$. Using the Berezin-Toeplitz Quantization, we get

\begin{equation}
\begin{split}
t_{m,n} &= A_{m,n}^N\int^{2\pi}_{0} \! \int^{1}_{0}\delta_{\gamma}(x,p)e^{i(n-m)x}e^{(n+m)p-Np^{2}} \,dp \,dx \\ \nonumber
&= A_{m,n}^N\int_{\gamma} e^{i(n-m)x}e^{(n+m)p-Np^{2}} \,ds
\end{split}
\end{equation} Using the parametrization $x = 2\pi\cos(t), p = \sin(t), ds = \sqrt{\frac{dx}{dt}^2 + \frac{dp}{dt}^2}dt, 0\le t \le \frac{\pi}{2}$, we get
\begin{equation}
t_{m,n} = A_{m,n}^N\int_{0}^{\frac{\pi}{2}} e^{i(n-m)2\pi\cos(t)}e^{(n+m)\sin(t)-N\sin^{2}(t)}\sqrt{(-2\pi\sin(t))^2 + cos^2(t)} \,dt
\end{equation}

Using MATLAB to graph the eigenvalues of these matrices for varying N, it is necessary to use numerical integration, specifically adapative Simpson quadrature in this instance, to get compile times under 8 hours.  When computing the matrix for $N\approx 68$, a singularity occurs in the quadrature process, causing an invalid approximation to occur, which can be seen in the following normalized graph: 
\begin{figure} [H]
\centerline{\includegraphics[scale=.77]{eigenvalues_D_ellipse_75_norm}}
\caption{Spectrum of the Dirac Delta Function assoc. Ellipse}
\end{figure}

 Our overarching goal is still to find a function that explain this distribution, and in doing so generalize the Szeg\"{o} limit theorem.  The case of the ellipse, however, presents is complicated enough that it makes sense to simply even further.  With this in mind we consider a much more basic example from which we hope to further.

Let $\begin{cases} x =t, 0\le t\le 2\pi \\ p = p, p \in \mathbb{R} \end{cases}$ .  Using the Berezin-Toeplitz Quantization, we get

\begin{equation}
\begin{split}
t_{m,n} &= A_{m,n}^N\int^{2\pi}_{0} \! \int^{1}_{0}\delta_{\gamma}(x,p)e^{i(n-m)x}e^{(n+m)p-Np^{2}} \,dp \,dx \\ \nonumber
&= A_{m,n}^Ne^{(n+m)p-Np^{2}}\int_0^{2\pi}e^{i(n-m)t} \,dt \\
&= 2\pi A_{m,n}^N\delta_{mn}e^{(n+m)p-Np^{2}}
\end{split}
\end{equation} where $\delta_{mn}$ is the Kroenecker Delta.  This eventually simplifies to  \begin{equation}
\begin{split}
t_{m,n}&=\delta_{mn}\sqrt{\frac{N}{\pi}}e^{-(\sqrt{N}p-\frac{n}{\sqrt{N}})^2}
\end{split}
\end{equation} Since we are dealing with a diagonal $n\times n$ matrix, we have the property that the $n^{th}$ eigenvalue is equivalent to the value in the $n^{th}$ row and $n^{th}$ column of the matrix.  After normalizing, we are left with
\begin{equation}
\lambda_n^{(N)} = e^{-(\sqrt{N}p-\frac{n}{\sqrt{N}})^2} \label{SEXY}
\end{equation} and the following graph: \begin{figure} [H]
\centerline{\includegraphics[scale=.75]{eigenvalues_D_x=t_p=p_normalized}}
\caption{Asymptotic expansion}
\end{figure}

We now direct our attention to the Szeg\"{o} Limit Theorem.  Let $\mathcal{W} \in C^{o}(\mathbb{R})$, where $C^{o}(\mathbb{R})$ is the space of continuous functions on $\mathbb{R}$.  We are interested in replicating the relationship derivied in Equation $\ref{BIGGUY}$, the Generalized Szeg\"{o} Corollary. Specifically, consider

\begin{equation}
 \lim_{N\to\infty}\frac{1}{N}\displaystyle\sum\limits_{k=1}^{N}\mathcal{W}(\lambda_{k}^{(N)}) 
\end{equation}  We substitute $\lambda_k^{(N)}$ with Equation \ref{SEXY} to get

\begin{equation} 
\lim_{N\to\infty}\frac{1}{N}\displaystyle\sum\limits_{k=1}^{N}\mathcal{W}(e^{-(\sqrt{N}p-\frac{k}{\sqrt{N}})^2}) \label{SEXIER}
\end{equation} If we let

\begin{equation} 
f_N(u) = e^{-(\sqrt{N}p-u)^2} 
\end{equation} and split $\frac{1}{N}$ into two equal parts then Equation \ref{SEXIER} becomes

\begin{equation} 
\frac{1}{\sqrt{N}}\lim_{N\to\infty}\displaystyle\sum\limits_{k=1}^{N}\mathcal{W} \circ f_{N}\left(\frac{k}{\sqrt{N}}\right)\frac{1}{\sqrt{N}}
\end{equation}  If we view this as a Riemann Sum, then we can rewrite it as

\begin{equation} 
\frac{1}{\sqrt{N}}\int_0^{\sqrt{N}}\mathcal{W}(e^{-(\sqrt{N}p-u)^2})\,du 
\end{equation}  Applying the change of variable $t = \frac{u-\sqrt{N}p}{\sqrt{N}}$, we are left with

\begin{equation} 
\int_{-p}^{1-p}\mathcal{W}(e^{-Nt^2})\,dt 
\end{equation} As $N\to\infty$, this expression goes to 0, which gives us little information about our desired distribution function. Fortunately, however, using asymptotic analysis we can approximate this integral to get a better idea of what is occuring.

To start off with the simplest case, let $$\mathcal{W}(x) = x^k$$.  We then have $$\int_{-p}^{1-p}e^{-kNt^2}\,dt$$ which can be split up into $$\int_0^{p}e^{-kNt^2}\,dt + \int_0^{1-p}e^{-kNt^2}\,dt$$ and the bounds on the first integral are correct because $e^{-kNt^2}$ is an even function.  Applying the change of variable $s = \sqrt{kN}t$ we get

\begin{equation} 
\begin{split} 
& \frac{1}{\sqrt{kN}}\left(\int_0^{\sqrt{kN}p}e^{-s^2}\,ds + \int_0^{\sqrt{kN}(1-p)}e^{-s^2}\,ds\right) \\ &= \frac{1}{2}\sqrt{\frac{\pi}{kN}}\left(erf\left(\sqrt{kN}p + erf\left(\sqrt{kN}(1-p)\right)\right)\right)
 \end{split}
 \end{equation}  Using asympstotic expansion, this approximately equals

\begin{equation} 
\label{NO}
\frac{1}{2}\sqrt{\frac{\pi}{kN}}\left[ 2 + e^{-kNp^2}(a_n) + e^{-kn(1-p)^2}(b_n) \right] 
\end{equation} where

\begin{equation}
a_n = \displaystyle\sum\limits_{n=0}^{\infty} (-1)^{n+1}\frac{(2n-1)!!}{2^n (\sqrt{kN}p)^{2n+1}}
\end{equation}

\begin{equation}
b_n = \displaystyle\sum\limits_{n=0}^{\infty} (-1)^{n+1} \frac{(2n-1)!!}{2^n(\sqrt{kN}(1-p))^{2n+1}}
\end{equation}

Simultaneously we consider the same integral from before: $$\int_{-p}^{1-p}\mathcal{W}(e^{-Nt^2})\,dt$$ but with a different change of variables, this time $$s = e^{-Nt^2}$$  We get

\begin{equation}
\label{ohyeah}
\frac{1}{2\sqrt{N}}\left[\int_{e^{-Np^2}}^{1} \frac{\mathcal{W}(s)}{s\sqrt{-\log s}}\,ds + \int_{e^{-N(1-p)^2}}^{1} \frac{\mathcal{W}(s)}{s\sqrt{-\log s}}\,ds\right]
\end{equation}  If we let $\mathcal{W}(s) = s^k$ once again, then this simplifies to

\begin{equation}
\frac{1}{2\sqrt{N}}\left[\int_{e^{-Np^2}}^{1} \frac{s^{k-1}}{\sqrt{-\log s}}\,ds + \int_{e^{-N(1-p)^2}}^{1} \frac{s^{k-1}}{\sqrt{-\log s}}\,ds\right]
\end{equation}  Using the fact that

\begin{equation}
\int_{0}^{1} \frac{s^{k-1}}{\sqrt{-\log s}}\,ds = \sqrt{\frac{\pi}{k}}
\end{equation} we can simplify equation \ref{ohyeah} to

\begin{equation}
\frac{1}{2\sqrt{N}}\left(2\sqrt{\frac{\pi}{k}}\right) = \sqrt{\frac{\pi}{kN}}
\end{equation}

Notice that $\sqrt{\frac{\pi}{kN}}$ is the same leading term from our asymptotic expansion from Equation \ref{NO}.  We use this as motivation for our theorem and its proof.

\begin{proof}
Lemons
\end{proof}

\end{document}

### 2015-04-09 draft.tex
added includes

--- 2015-04-05 Introduction_trying.tex
@@
 \usepackage{amsthm}
-\usepackage{graphicx}
-\usepackage{caption}
-\usepackage{epstopdf}
-\usepackage{float}
+%\usepackage{graphicx}
+%\usepackage{caption}
+%\usepackage{epstopdf}
+%\usepackage{float}
 
-\title{Toeplitz Matrices, Szeg\"{o} Limit Theorem}
+\title{Exploring Bounds}
 \author{Tyler Friedman}
-
-\newtheorem{mydef}{Definition}[section]
-\newtheorem{theorem}{Theorem}[section]
-\newtheorem{corollary}[theorem]{Corollary}
-\newtheorem{proposition}[theorem]{Proposition}
-\newtheorem{claim}[theorem]{Claim}
-
-\newtheorem{exmp}{Example}[section]
 
@@
 
-\section{Introduction}
+HELLO!
 
-Suppose $f(x,p)$ :   $\mathbb{R}^{2}  \rightarrow \mathbb{R}$ is a real-valued function defined on the cylinder s.t.
-$-\pi \le x \le \pi,  0 \le p \le 1$.
-We can then define the Fourier series of such a function:
-\begin{equation}
-f(x,p) = \displaystyle\sum\limits_{k=-\infty}^\infty f_{k}(p)e^{ikx} \label{fourier}
-\end{equation}
-Suppose we then arrange the coefficients of this Fourier series, the $f_{k}(p)$, into a $Toeplitz$ matrix.
-
-\begin{mydef}
-A Toeplitz matrix is an $n\times n$ matrix of the form 
-\[
-A = 
-\begin{pmatrix}
-a_{0} & a_{1} & a_{2} & \cdots & \cdots & a_{n-1} \\
-a_{-1} & a_{0} & a_{1} & \ddots &  & \vdots \\
-a_{-2} & a_{-1} & \ddots & \ddots & \ddots & \vdots \\
-\vdots & \ddots & \ddots & \ddots & a_{1} & a_{2} \\
-\vdots &  & \ddots & a_{-1} & a_{0} & a_{1} \\
-a_{-n+1} & \cdots & \cdots & a_{-2} & a_{-1} & a_{0}
-\end{pmatrix}
-\]
-where $a_{i,j} = a_{i+1,j+1}, 1 \le i,j \le n$
-\end{mydef}
-
-\section{Weyl Quantization}
-In particular, suppose we form a variant of the Toeplitz matrix, the Szeg\"{o} -Toeplitz matrix, $T_{f,N}$, $N \ge 1$, where
-\begin{equation}
-t_{i,j} = f_{j-i}(\frac{1}{2}\ \frac{i+j}{N+1}), 1 \le i,j \le N+1 \label{szegomap}
-\end{equation}
-
-The eigenvalues of such a matrix is an area of considerable interest.
-For example.
-consider the normalized function $f(x,p) = (\cos(x) + p\sin(x))/\sqrt{2}$ with domain defined as above.
-The specturm of $T_{f,N}$, as N varies from $1$ to $\infty$ gives us the following graph:
-
-\begin{figure} [H]
-\centerline{\includegraphics{cosx+psinx}}
-\caption{Distribution of eigenvalues}
-\end{figure}
-
-Notice how the eigenvalues become more concentrated around $\pm0.7$ as $N \rightarrow \infty$.
-Our goal is to find some function that describes the distribution of these eigenvalues, and can explain why they become so densely populated at certain points.
-With this is in mind, we begin by utilitzing the Szeg\"{o}-Limit Theorem.
-
-\begin{theorem} \emph{(Szeg\"{o}-Limit Theorem)} \label{Szego} If f is not horrible, then $\forall k \ge 1, k \in \mathbb{Z}$: \begin{equation}
-\lim_{N \to \infty} \frac{1}{N+1} Tr((T_{f,N})^k) = \frac{1}{2\pi} \int^{\pi}_{-\pi} \! \int^1_0  f_{f,N}(x,p)^k \,dp \,dx \label{szego}
-\end{equation} 
-\end{theorem}
-
- Because $T_{f,N}$ is Hermitian, it can be diagonlized.  Using this property, along with the fact that $Tr(AB) = Tr(BA)$, it is not difficult to rewrite Equation \ref{szego} as
-
-\begin{equation} 
-\lim_{N \to \infty} \frac{1}{N+1} \displaystyle\sum\limits_{j=0}^{N} (\lambda_{j}^{(N)})^k= \frac{1}{2\pi} \int^{\pi}_{-\pi} \! \int^1_0  f_{f,N}(x,p)^k \,dp \,dx 
-\end{equation} Further, it can be shown that this slightly altered form of the Szeg\"{o}-Limit Theorem is in fact just one instance of a more powerful equality.  In general:
-
-\begin{corollary}
-If $\varphi \ cont:[-1,1] \rightarrow \mathbb{R}$, then
-\begin{equation}
-\lim_{N \to \infty} \frac{1}{N+1}  \displaystyle\sum\limits_{j=0}^N \varphi(\lambda_{j}^{(N)})= \frac{1}{2\pi} \int^{\pi}_{-\pi} \! \int^1_0  \varphi(f_{f,N}(x,p)) \,dp \,dx \label{BIGGUY}
-\end{equation}
-\end{corollary}
-
-Consider the left side of this equation to be in the form of a Riemman sum. If the $\lambda_{j}^{(N)}$ were evenly distributed, we would be able to rewrite this equation as
-
-\begin{equation} 
-\int^1_{-1} \varphi(t) \,dt 
-\end{equation} Yet, from Figure 1 we can tell that this is not the case; consequently, we must compensate for this unequal distribution with some correction function, $\beta(t)$ s.t.
-
-\begin{equation}
-\lim_{N \to \infty} \frac{1}{N+1}  \displaystyle\sum\limits_{j=0}^N \varphi(\lambda_{j}^{(N)}) = \int^1_{-1} \varphi(t) \beta (t) \,dt \label{HOW}
-\end{equation} This function, $\beta(t)$, is exactly the function that will describe the distribution of our eigenvalues. WHY? NEED EXPLANATION.  Combining Equations \ref{BIGGUY} and \ref{HOW} we get
-
-\begin{equation} 
-\int^{\pi}_{-\pi} \! \int^1_0  \varphi(f_{f,N}(x,p)) \,dp \,dx = \int^1_{-1} \varphi(t) \beta (t) \,dt \label{beta} 
-\end{equation}
-
-To solve for $\beta(x)$  using exact methods, we can consider using the Coarea formula.
-
-\begin{theorem}
-\emph{(Coarea formula)} \label{coarea}
-Suppose that $\Omega$ is an open set in $\mathbb{R}^{n}$, and f is a real-valued Lipshitz function on $\Omega$.  Then, for an $L^{1}$ function $\Psi$,
-\begin{equation}
-\iint\limits_\Omega \Psi(x)\lvert\nabla f(x)\rvert \,dx =  \int_{Im(f)} \! (\int_{f^{-1}(x)} \Psi \,ds) \,dx
-\end{equation}
-\end{theorem}
-
-For our purposes, we can let
-
-\begin{equation} 
-\Psi = \frac{\varphi(f(x,p))}{\lvert\nabla f(x,p)\rvert} 
-\end{equation} and
-
-\begin{equation} 
-\Omega = [-\pi,\pi] \times [0,1] 
-\end{equation} We can then rewrite the left side of Equation \ref{beta} as 
-\begin{equation} \begin{split} 
-\int^{\pi}_{-\pi} \! \int^1_0  \varphi(f_{f,N}(x,p)) \,dp \,dx& =  \iint\limits_\Omega \Psi\lvert\nabla f \rvert\, dp \, dx  \\ 
-& = \int_{Im(f)} \! \left(\int_{f^{-1}(t)} \frac{\varphi(f(x,p))}{\lvert\nabla f(x,p)\rvert} \,ds\right) \,dt    \text{ $...$ by the Coarea fomula} \\
-& = \int_{Im(f)} \!
-\left(\int_{f^{-1}(t)} \frac{\varphi(t)}{\lvert\nabla f(x,p)\rvert} \,ds\right) \,dt\\ & = \int_{Im(f)} \varphi(t) \!
-\left(\int_{f^{-1}(t)} \frac{1}{\lvert\nabla f(x,p)\rvert} \,ds\right) \,dt \end{split}
-\end{equation} Notice that the inner integral is exactly the $\beta(x)$ that we originally set out to find:
-
-\begin{equation}
-\beta(x) = \int_{f^{-1}(t)} \frac{1}{\lvert\nabla f(x,p)\rvert} \,ds
-\end{equation}
-
-With that said, we know of no reasonable method to analytically compute such an integral.
-Thus instead we focus our attention on approximating this unknown distribution function.
-Our method of choice is orthogonal polynomials, specifically the normalized $Legendre$ polynomial.
-It is important to note that  these polynomials are only orthogonal on the interval $[-1,1]$, and thus that is the only interval on which our approximation will  make sense.
-
-Let 
-\begin{equation} 
-\beta (x) = \displaystyle\sum\limits_{n=0}^N a_n P_n(x) 
-\end{equation} where
-
-\begin{equation} 
-a_n = \int^1_{-1} \beta (x) P_n(x) \, dx,\  P_n = \lvert\lvert{p_n}\rvert\rvert 
-\end{equation} and the unnormalized Legendre polynomials, $p_n$, are
-
-\begin{equation} 
-1, x, \frac{1}{2}(3x^2 - 1), \frac{1}{2}(5x^3 -3x), \frac{1}{8}(35x^4 - 30x^2 + 3), \cdots 
-\end{equation} Using the equality from Equation \ref{beta}, we can rewrite $a_n$ as
-
-\begin{equation} 
-a_n = \int^{\pi}_{-\pi} \! \int^1_0  P_n(f_{f,N}(x,p)) \,dp \,dx
-\end{equation} Using this approximation, we find the graph of $\beta (x)$ from our initial example to be
-
-\begin{figure} [H] 
-\centerline{\includegraphics[scale=.50]{legendre_apprx2}} 
-\caption{Distribution approximation function} 
-\end{figure} Notice the two peaks around $\pm0.7$.  This is consistent with our data from Figure 1, in which the eigenvalues are most densely distributed at those two numbers.
-
-Another interesting case to consider is where the Szeg\"{o}-Toeplitz matrix formed has non-zero values everywhere, as opposed to the previous example where only two diagonals contained such values.
-Let $$f(x,p) = xp, [-\pi,\pi]\times[0,1]$$ \begin{figure} [H] \centerline{\includegraphics[scale=.60]{eigenvalues_xp}} \caption{eigenvalues for given N} \end{figure} \clearpage \begin{figure} [H] \centerline{\includegraphics[scale=.50]{legendre_apprx_xp}} \caption{Distribution approximation function} \end{figure}  Once again we find that the peak of our distribution approximation function corresponds exactly to the area of highest concentration among eigenvalues in the spectrum.
-
-We have just provided
-
-\section{Berezin-Toeplitz Quantization}
-
-While very interesting, the Weyl quantization method applies only to real-valued functions, and the true focus of this research is understanding the distributions of much more interesting functions.
-We are consequently motivated to define a different quantization method, the Berezin-Toeplitz Quantization, which will allow us to explore more interesting cases.
-To do so, we begin by considering the domain $(x,p)\in [0,2\pi]\times\mathbb{R}$, and imposing a complex variable z s.t.
-$z = x-ip \in \mathbb{C}$.
-We can then form a geometric quantization to the Bergmann Space, $\mathcal{B}$, of the cylinder where $\mathcal{B} = \Psi(z)$, defined s.t.
-\begin{enumerate}
-\item $\Psi$ is analytic, i.e. $\Psi$ is not a function of $\overline{z}$
-\item $\Psi$ is periodic in $z$, i.e. $\Psi(z + 2\pi) = \Psi(z)$
-\item $\lvert\lvert\Psi\rvert\rvert^2 =  \int^{2\pi}_{0} \! \int^{\infty}_{-\infty}  \lvert\Psi(z)\rvert^{2}e^{-Np^{2}} \,dp \,dx< \infty, N=\frac{1}{\hbar}$
-\end{enumerate}
-
-We define the Hermitian inner product on $\mathcal{B}$ s.t.
-
-$$ \forall \Psi_{1},\Psi_{2} \in \mathcal{B}, \langle\Psi_{1},\Psi_{2}\rangle = \int^{2\pi}_{0} \! \int^{\infty}_{-\infty}  \Psi_{1}(z)\overline{\Psi_{2}(z)}e^{-Np^{2}} \,dp \,dx$$
-
-Our goal is now to find an orthonormal basis of $\mathcal{B}$, which we can use to define the Berezin-Toeplitz operator.
-\begin{proposition} $\forall n \in\mathbb{Z}, e^{inz}\in\mathcal{B}$ \end{proposition} We see how this is true because this generalized vector fulfills the three conditions we just set out for $\mathcal{B}$ :
-
-\begin{enumerate}
-\item 
-$e^{inz} = \displaystyle\sum\limits_{k=0}^\infty \frac{1}{k!}(inz)^k$ by Taylor's theorem.  There are clearly no $\overline{z}$.
-
-\item
-\begin{equation*}
-\begin{split}
-e^{in(z+2\pi)} &= e^{inz} e^{in2\pi} \\
-& = e^{inz}\cdot 1 \\
-& = e^{inz}
-\end{split}
-\end{equation*}
-
-\item 
-It can be shown through fairly straightforward calculation that 
-\begin{equation}
-\lvert\lvert e^{inz}\rvert\rvert^2 = \frac{2\pi^{3/2}}{N^{\frac{1}{4}}}e^{\frac{\pi^2}{2N}} < \infty \label{normalizer}
-\end{equation}
-\end{enumerate} Since we are looking for an orthonormal basis, we divide by the length of $e^{inz}$ found in Equation \ref{normalizer}.
-
-\begin{mydef}
-$\forall n \in \mathbb{Z}, e_{n}(z) := \frac{e^{inz}}{\sqrt{T}}, T = \frac{2\pi^{3/2}}{N^{\frac{1}{4}}}e^{\frac{\pi^2}{2N}}$
-\end{mydef} From our definition of $e_n(z)$, it follows shortly thereafter that  $\langle e^{inz},e^{imz}\rangle = \delta_{nm}$, and consequently we can claim that $\{e_n | n\in \mathbb{Z}\}$ is an orthonormal basis of $\mathcal{B}$.
-
-Let $\mathcal{H} = span\{e_n |\, 0\le n \le N\}$.  Then take $f: [0,2\pi]\times\mathbb{R} \rightarrow\mathbb{R}$, and we are now able to define the Berezin-Toeplitz Operator of $f$
-
-\begin{mydef}
-\emph{(Berezin-Toeplitz Operator)}
-$Op(f):\Psi \rightarrow f\Psi\rightarrow\Pi(f\Psi)$, where $\Pi$ is the othogonal projection of $\Psi$  onto $\mathcal{B}$
-\end{mydef}
-
-In other words, the operator takes an element of $\mathcal{B}$ and hits it with $f$, but because $f\Psi\notin\mathcal{B}$ (consider $f(x,p) = cosx + psinx$), we must then project back onto the Bergmann space, hence the orthogonal projection.
-
-We can rewrite
-
-\begin{equation}
-\Pi(f\Psi) = \displaystyle\sum\limits_{n=0}^N\langle f\Psi,e_n\rangle e_n
-\end{equation}
-
-We now want to find the matrix of $Op(f)$ $w.r.t$ $\{e_n| n=0,1,2,\cdots,N\}$
-
-\begin{equation}
-\begin{split}
-t_{m,n} &= \langle Op(f)(e_n),e_m\rangle \\
-& =\langle fe_n,e_m\rangle \text{$\cdots$ because $\Pi$ is adjoint} \\
-& = \frac{\sqrt{N}}{2\pi^{\frac{3}{2}}}e^{-\frac{n^2+m^2}{2N}}  \int^{2\pi}_{0} \! \int^{\infty}_{-\infty}f(x,p)e^{in(x-ip)}\overline{e^{im(x-ip)}}e^{-Np^{2}} \,dp \,dx \\
-& =  \frac{\sqrt{N}}{2\pi^{\frac{3}{2}}}e^{-\frac{n^2+m^2}{2N}}  \int^{2\pi}_{0} \! \int^{\infty}_{-\infty}f(x,p)e^{i(n-m)x}e^{(n+m)p-Np^{2}} \,dp \,dx
-\end{split}
-\end{equation}
-
-Recall that $\mathcal{H} = span\{e_n, 0\le n \le N\}$.
-If we rewrite the range of $n$ as $0\le \frac{n}{N} \le 1$, then $\mathcal{H}$ can be thought of as the span\{eigenvectors of Op(p) with eigenvalues in $[0,1]$\}.
-Hence we can rewrite the quantization as
-
-\begin{equation}
-\frac{\sqrt{N}}{2\pi^{\frac{3}{2}}}e^{-\frac{n^2+m^2}{2N}}  \int^{2\pi}_{0} \! \int^{1}_{0}f(x,p)e^{i(n-m)x}e^{(n+m)p-Np^{2}} \,dp \,dx
-\end{equation} using the corresponding classical region as was used with the Weyl Quantization.
-This final result is the Berezin-Toeplitz quantization we originally set out to find.
-Notice that to this point we have made no assumptions about $f$ being real valued.
-
-\section{Dirac Delta Function}
-
-For simplicity, let
-$$A_{m,n}^N = \frac{\sqrt{N}}{2\pi^{\frac{3}{2}}}e^{-\frac{n^2+m^2}{2N}}$$ Using the Berezin-Toeplitz Quanitzation, we are now able to to consider the spectrum of more interesting functions.
-The most elementary such function we can consider is the Dirac Delta Function.
-For this generalized function, we find its matrix to be
-
-\begin{equation} 
-\begin{split} 
-t_{m,n} &=  A_{m,n}^N\int^{2\pi}_{0} \! \int^{1}_{0}\delta(x_{0},p_{0})e^{i(n-m)x}e^{(n+m)p-Np^{2}} \,dp \,dx \\ 
-&=A_{m,n}^Ne^{i(n-m)x_{0}}e^{(n+m)p_{0}-Np_{0}^{2}} 
-\end{split} 
-\end{equation} For $x_{0} = 1, p_{0} = 1/3$, we get
-
-\begin{figure} [H]\centerline{\includegraphics[scale=.62]{eigenvalues_delta}} \caption{Spectrum of the Dirac Delta Function} \end{figure} From the graph we conclude that the delta function is a linear projector (?) times a linearly increasing constant in the context of the B-T quantization.
-
-Motivated by finding a more interesting case, we now study the more slightly more complicated Dirac Delta Function associated with a Curve.
-
-\begin{mydef} The Dirac Delta Function associated with a Curve, $\delta_{\gamma}$, is the generalized function s.t.
-$\forall\ \varphi: [0,2\pi] \times \mathbb{R} \rightarrow \mathbb{R}$ "nice", $$  \int^{2\pi}_{0} \!
-\int^{1}_{0}\delta_{\gamma}(x,p)\varphi(x,p) \,dp \,dx \\ = \int_{\gamma} \varphi \,ds$$
-\end{mydef} The simplest curve to consider for our domain is the ellipse
-
-\begin{equation} 
-\left(\frac{x}{2\pi}\right)^2 + p^2  = 1, \nonumber 
-\end{equation} where $0\le x\le\frac{\pi}{2}, 0\le p \le 1$. Using the Berezin-Toeplitz Quantization, we get
-
-\begin{equation}
-\begin{split}
-t_{m,n} &= A_{m,n}^N\int^{2\pi}_{0} \! \int^{1}_{0}\delta_{\gamma}(x,p)e^{i(n-m)x}e^{(n+m)p-Np^{2}} \,dp \,dx \\ \nonumber
-&= A_{m,n}^N\int_{\gamma} e^{i(n-m)x}e^{(n+m)p-Np^{2}} \,ds
-\end{split}
-\end{equation} Using the parametrization $x = 2\pi\cos(t), p = \sin(t), ds = \sqrt{\frac{dx}{dt}^2 + \frac{dp}{dt}^2}dt, 0\le t \le \frac{\pi}{2}$, we get
-\begin{equation}
-t_{m,n} = A_{m,n}^N\int_{0}^{\frac{\pi}{2}} e^{i(n-m)2\pi\cos(t)}e^{(n+m)\sin(t)-N\sin^{2}(t)}\sqrt{(-2\pi\sin(t))^2 + cos^2(t)} \,dt
-\end{equation}
-
-Using MATLAB to graph the eigenvalues of these matrices for varying N, it is necessary to use numerical integration, specifically adapative Simpson quadrature in this instance, to get compile times under 8 hours.
-When computing the matrix for $N\approx 68$, a singularity occurs in the quadrature process, causing an invalid approximation to occur, which can be seen in the following normalized graph:
-\begin{figure} [H]
-\centerline{\includegraphics[scale=.77]{eigenvalues_D_ellipse_75_norm}}
-\caption{Spectrum of the Dirac Delta Function assoc. Ellipse}
-\end{figure}
-
- Our overarching goal is still to find a function that explain this distribution, and in doing so generalize the Szeg\"{o} limit theorem.
-The case of the ellipse, however, presents is complicated enough that it makes sense to simply even further.
-With this in mind we consider a much more basic example from which we hope to further.
-
-Let $\begin{cases} x =t, 0\le t\le 2\pi \\ p = p, p \in \mathbb{R} \end{cases}$ .  Using the Berezin-Toeplitz Quantization, we get
-
-\begin{equation}
-\begin{split}
-t_{m,n} &= A_{m,n}^N\int^{2\pi}_{0} \! \int^{1}_{0}\delta_{\gamma}(x,p)e^{i(n-m)x}e^{(n+m)p-Np^{2}} \,dp \,dx \\ \nonumber
-&= A_{m,n}^Ne^{(n+m)p-Np^{2}}\int_0^{2\pi}e^{i(n-m)t} \,dt \\
-&= 2\pi A_{m,n}^N\delta_{mn}e^{(n+m)p-Np^{2}}
-\end{split}
-\end{equation} where $\delta_{mn}$ is the Kroenecker Delta.  This eventually simplifies to  \begin{equation}
-\begin{split}
-t_{m,n}&=\delta_{mn}\sqrt{\frac{N}{\pi}}e^{-(\sqrt{N}p-\frac{n}{\sqrt{N}})^2}
-\end{split}
-\end{equation} Since we are dealing with a diagonal $n\times n$ matrix, we have the property that the $n^{th}$ eigenvalue is equivalent to the value in the $n^{th}$ row and $n^{th}$ column of the matrix.
-After normalizing, we are left with
-\begin{equation}
-\lambda_n^{(N)} = e^{-(\sqrt{N}p-\frac{n}{\sqrt{N}})^2} \label{SEXY}
-\end{equation} and the following graph: \begin{figure} [H]
-\centerline{\includegraphics[scale=.75]{eigenvalues_D_x=t_p=p_normalized}}
-\caption{Asymptotic expansion}
-\end{figure}
-
-We now direct our attention to the Szeg\"{o} Limit Theorem.
-Let $\mathcal{W} \in C^{o}(\mathbb{R})$, where $C^{o}(\mathbb{R})$ is the space of continuous functions on $\mathbb{R}$.
-We are interested in replicating the relationship derivied in Equation $\ref{BIGGUY}$, the Generalized Szeg\"{o} Corollary.
-Specifically, consider
-
-\begin{equation}
- \lim_{N\to\infty}\frac{1}{N}\displaystyle\sum\limits_{k=1}^{N}\mathcal{W}(\lambda_{k}^{(N)}) 
-\end{equation}  We substitute $\lambda_k^{(N)}$ with Equation \ref{SEXY} to get
-
-\begin{equation} 
-\lim_{N\to\infty}\frac{1}{N}\displaystyle\sum\limits_{k=1}^{N}\mathcal{W}(e^{-(\sqrt{N}p-\frac{k}{\sqrt{N}})^2}) \label{SEXIER}
-\end{equation} If we let
-
-\begin{equation} 
-f_N(u) = e^{-(\sqrt{N}p-u)^2} 
-\end{equation} and split $\frac{1}{N}$ into two equal parts then Equation \ref{SEXIER} becomes
-
-\begin{equation} 
-\frac{1}{\sqrt{N}}\lim_{N\to\infty}\displaystyle\sum\limits_{k=1}^{N}\mathcal{W} \circ f_{N}\left(\frac{k}{\sqrt{N}}\right)\frac{1}{\sqrt{N}}
-\end{equation}  If we view this as a Riemann Sum, then we can rewrite it as
-
-\begin{equation} 
-\frac{1}{\sqrt{N}}\int_0^{\sqrt{N}}\mathcal{W}(e^{-(\sqrt{N}p-u)^2})\,du 
-\end{equation}  Applying the change of variable $t = \frac{u-\sqrt{N}p}{\sqrt{N}}$, we are left with
-
-\begin{equation} 
-\int_{-p}^{1-p}\mathcal{W}(e^{-Nt^2})\,dt 
-\end{equation} As $N\to\infty$, this expression goes to 0, which gives us little information about our desired distribution function.
-Fortunately, however, using asymptotic analysis we can approximate this integral to get a better idea of what is occuring.
-
-To start off with the simplest case, let $$\mathcal{W}(x) = x^k$$.
-We then have $$\int_{-p}^{1-p}e^{-kNt^2}\,dt$$ which can be split up into $$\int_0^{p}e^{-kNt^2}\,dt + \int_0^{1-p}e^{-kNt^2}\,dt$$ and the bounds on the first integral are correct because $e^{-kNt^2}$ is an even function.
-Applying the change of variable $s = \sqrt{kN}t$ we get
-
-\begin{equation} 
-\begin{split} 
-& \frac{1}{\sqrt{kN}}\left(\int_0^{\sqrt{kN}p}e^{-s^2}\,ds + \int_0^{\sqrt{kN}(1-p)}e^{-s^2}\,ds\right) \\ &= \frac{1}{2}\sqrt{\frac{\pi}{kN}}\left(erf\left(\sqrt{kN}p + erf\left(\sqrt{kN}(1-p)\right)\right)\right)
- \end{split}
- \end{equation}  Using asympstotic expansion, this approximately equals
-
-\begin{equation} 
-\label{NO}
-\frac{1}{2}\sqrt{\frac{\pi}{kN}}\left[ 2 + e^{-kNp^2}(a_n) + e^{-kn(1-p)^2}(b_n) \right] 
-\end{equation} where
-
-\begin{equation}
-a_n = \displaystyle\sum\limits_{n=0}^{\infty} (-1)^{n+1}\frac{(2n-1)!!}{2^n (\sqrt{kN}p)^{2n+1}}
-\end{equation}
-
-\begin{equation}
-b_n = \displaystyle\sum\limits_{n=0}^{\infty} (-1)^{n+1} \frac{(2n-1)!!}{2^n(\sqrt{kN}(1-p))^{2n+1}}
-\end{equation}
-
-Simultaneously we consider the same integral from before: $$\int_{-p}^{1-p}\mathcal{W}(e^{-Nt^2})\,dt$$ but with a different change of variables, this time $$s = e^{-Nt^2}$$  We get
-
-\begin{equation}
-\label{ohyeah}
-\frac{1}{2\sqrt{N}}\left[\int_{e^{-Np^2}}^{1} \frac{\mathcal{W}(s)}{s\sqrt{-\log s}}\,ds + \int_{e^{-N(1-p)^2}}^{1} \frac{\mathcal{W}(s)}{s\sqrt{-\log s}}\,ds\right]
-\end{equation}  If we let $\mathcal{W}(s) = s^k$ once again, then this simplifies to
-
-\begin{equation}
-\frac{1}{2\sqrt{N}}\left[\int_{e^{-Np^2}}^{1} \frac{s^{k-1}}{\sqrt{-\log s}}\,ds + \int_{e^{-N(1-p)^2}}^{1} \frac{s^{k-1}}{\sqrt{-\log s}}\,ds\right]
-\end{equation}  Using the fact that
-
-\begin{equation}
-\int_{0}^{1} \frac{s^{k-1}}{\sqrt{-\log s}}\,ds = \sqrt{\frac{\pi}{k}}
-\end{equation} we can simplify equation \ref{ohyeah} to
-
-\begin{equation}
-\frac{1}{2\sqrt{N}}\left(2\sqrt{\frac{\pi}{k}}\right) = \sqrt{\frac{\pi}{kN}}
-\end{equation}
-
-Notice that $\sqrt{\frac{\pi}{kN}}$ is the same leading term from our asymptotic expansion from Equation \ref{NO}.  We use this as motivation for our theorem and its proof.
-
-\begin{proof}
-Lemons
-\end{proof}
+%First explore linear programming bound
+Krawtouck polynomials
 

### 2015-04-09 draft.tex
added notes

@@
 
-HELLO!
+\section{Introduction}
+
+There exists a considerable interest today in determining the maximum possible
+number of codewords for a code with certain parameters.  We use the notation $A_q(n,d)$
+and $B_q(n,d)$, defined as the maximum of number of codewords in a code over
+$\mathbb{F}_q$ of length $n$ and minimum distance $d$ for an arbitrary (linear
+on non-linear) code and linear code, respectively.  In lecture, we have
+considered upper bounds---Sphere Packing, Singleton, and Greismer---as well as
+lower bounds---Gilbert and Varshamov---on these values.  The purpose of this
+paper is to consider other well-known bounds in the literature.
+
+This paper is broken up into $x$ sections.
 
 %First explore linear programming bound
-Krawtouck polynomials
+Asymptotic singleton, include 2 examples
+Asymptotic plotkin, some examples
+draw graph
+Asymptotic hamming
+	define hilbert, prove 135,136, define vq(n,a),
+	black box 2.10.3, prove 2.10.5
 

### 2015-04-09 draft.tex
more notes

--- 2015-04-09 draft.tex
@@
 
-HELLO!
+\section{Introduction}
+
+An interesting problem in coding theory is how to determine the maximum possible
+number of codewords in a code.  For an $n$-dimensional code, we are interested in 
+the maximum number of codewords such that the code has weight $d$.  
+Formally, we use the notation $A_q(n,d)$
+and $B_q(n,d)$, defined as the maximum of number of codewords in a code over
+$\mathbb{F}_q$ of length $n$ and minimum distance $d$ for an arbitrary (linear
+on non-linear) code and linear code, respectively.  It is not always possible to In lecture, we have
+considered upper bounds---Sphere Packing, Singleton, and Greismer---as well as
+lower bounds---Gilbert and Varshamov---on these values.  The purpose of this
+paper is to consider other well-known bounds in the literature.
+
+This paper is broken up into $x$ sections.
 
 %First explore linear programming bound
-Krawtouck polynomials
+Asymptotic singleton, include 2 examples
+Asymptotic plotkin, some examples
+draw graph
+Asymptotic hamming
+	define hilbert, prove 135,136, define vq(n,a),
+	black box 2.10.3, prove 2.10.5
+
+Table of common$a_q(n,d)$ values
+Recall basic theory: thm 2.1.2, 2.1.6
+
+Sections
+
+Plotkin
+talk about importance
+define it
+prove it
+work out some examples
+
+Elias
+talk about importance
+define it
+prove two lemmas that do the heavy lifting
+easy proof to finish it off
+work out some examples
+
+Linear Programming Bound
+talk about importance
+define it
+prove it
+work out some examples
+
+Note existence of two lower bounds, say we talked about them in class
 

### 2015-04-09 draft.tex
added basic asymptotic bounds stuff

@@
 \usepackage{amsthm}
+
 %\usepackage{graphicx}
@@
 %\usepackage{float}
+
+\newtheorem{theorem}{Theorem}
+\numberwithin{theorem}{subsection}
 
@@
 This paper is broken up into $x$ sections.
+
+\section{Asymptotic Bounds}
+We now wish to consider these $A_q(n,d)$ values as n goes to infinity.  To do so, we must more formally define two terms.
+
+In class, we have considered the \textit{rate} of a linear code, $k/n$, as one measure of the goodness of a code.  That is,
+the rate tells us how much information relative to redundancy that our codewords provide.  The concept of rate can be generalized
+to non-linear codes as well.  For a possibly nonlinear code over $\mathbb{F}_q$ with $M$ codewords, the \textit{rate} is defined to be $n^{-1} \log_q {M}$.  Notice that
+for an $[n,k,d]$ linear code, $M = q^k$ and hence the rate is $k/n$ as we expect.
+
+A second notion of goodness that we have discussed, but I think not formally defined, is the \textit{relative distance} of a code.  For a linear or nonlinear code of length n
+has minimum distance d, this value is the ratio $d/n$.
+
+Consequently, for our asymptotic bounds, we are interested in the largest possible rate for a family of codes over $\mathbb{F}_q$ of lengths going to infinity with relative 
+distances approaching some constant $\delta$.  In other words, we consider the equation:
+
+\begin{equation}
+\alpha_{q}(\delta) = \limsup_{n \to \infty} n^{-1} \log_q A_q(n,\delta n)
+\end{equation}
+
+[What does this imply?]
+
+\subsection{Asymptotic Singleton Bound}
+
+Recall the Singleton Bound from lecture:
+
+\begin{theorem}
+For $d \le n$, $A_q(n,d) \le q^{n-d+1}$.
+\end{theorem}
+
+[explain what this means, what are the implications]
+
+\begin{theorem}
+If $0 \le \delta \le 1$, then $\alpha_q(\delta) \le 1 - \delta$.
+\end{theorem} 
+This theorem follows directly from the Singleton bound.
+
+\begin{proof}
+\begin{equation} 
+\begin{split}
+\alpha_{q}(\delta) & = \limsup_{n \to \infty} n^{-1} \log_q A_q(n,\delta n) \\
+& \le \limsup_{n \to \infty} n^{-1} \log_q q^{n-\delta n+1} \\
+& \le \limsup_{n \to \infty} \frac{n-\delta n+1}{n} \\
+& \le 1 - \delta
+\end{split}
+\end{equation}
+\end{proof}
+
+\subsection{Asymptotic Plotkin Bound}
 

### 2015-04-14 draft.tex
finished project description

@@
 \usepackage{amsthm}
+\usepackage{verbatim}
 
@@
 
-An interesting problem in coding theory is how to determine the maximum possible
-number of codewords in a code.  For an $n$-dimensional code, we are interested in 
-the maximum number of codewords such that the code has weight $d$.  
+An interesting problem in coding theory is determining the maximum
+number of codewords in a code with certain parameters.  For an $n$-dimensional code, we are interested in 
+the maximum number of codewords such that the code has minimum distance $d$.  
 Formally, we use the notation $A_q(n,d)$
-and $B_q(n,d)$, defined as the maximum of number of codewords in a code over
+and $B_q(n,d)$ to define the maximum of number of codewords in a code over
 $\mathbb{F}_q$ of length $n$ and minimum distance $d$ for an arbitrary (linear
-on non-linear) code and linear code, respectively.  It is not always possible to In lecture, we have
-considered upper bounds---Sphere Packing, Singleton, and Greismer---as well as
+on non-linear) code and linear code, respectively.
+
+For arbitrary $n$ and $d$, it is difficult to find $A_q(n,d)$ and $B_q(n,d)$ exactly.
+ In lecture, we have considered upper bounds---Sphere Packing, Singleton, and Greismer---as well as
 lower bounds---Gilbert and Varshamov---on these values.  The purpose of this
-paper is to consider other well-known bounds in the literature.
+paper is to take a survey of other well-known bounds in the literature that we have not discussed.  
+In the first part of the paper, we will consider the Plotkin Upper bound, 
+the Elias Upper bound, and the Linear Programming Upper Bound.  In the second part of the paper, we will consider asymptotic versions
+of Singleton, Plotkin, Hamming, and Elias.  (I am very certain that I won't get to discuss all of these bounds, but I am currently unsure how much space each discussion will take up so I've
+listed all that I am considering.)  For each bound, we will consider its proof as well
+as related examples.  Lastly, in the final part we will consider lexicodes, an interesting subset of linear codes that meet the Gilbert Bound.
 
-This paper is broken up into $x$ sections.
+Some implementation specific details: for the Linear Programming bound, I will introduce basic linear programming concepts and as well as the Krawtchouck polynomials.  For the 
+Asymptotic Hamming bound I will introduce the Hilbert entropy function.
+
+\begin{comment}
 
@@
 
+\end{comment}
+
 \end{document}

### 2015-04-14 draft.tex
almost finished with proof of Plotkin

@@
 
-\begin{comment}
+\section{Upper Bounds}
+
+\subsection{Plotkin Upper Bound}
+%Plotkin
+%talk about importance
+%define it
+%prove it
+%work out some examples
+
+The Plotkin Bound is an upper bound that often improves upon the Sphere Packing Bound on $A_q(n,d)$.  It is limited, however, in that it is only valid when $d$ is sufficiently
+close to $n$.  Consider that for $q=2$ our restriction is $n<2d$,  for $q=3$ our restriction is $n<\frac{3}{2}d$, for $q=4$ our restriction is $n<\frac{4}{3}d$, etc.  For large $q$, the
+number of codes we can consider becomes increasingly limited.
+
+\begin{theorem}[Plotkin]
+Let $C$ be an $(n,M,d)$ code over $\mathbb{F}_q$ such that $rn < d$ where $r = 1 - q^{-1}$.  Then
+\begin{equation}
+A_q(n,d) \le \left \lfloor \frac{d}{d-rn}\right\rfloor
+\end{equation}
+\end{theorem}
+
+\begin{proof}
+Let 
+\begin{equation} \label{plotkin_1}
+S = \sum_{x \in \mathcal{C}} \sum_{y \in \mathcal{C}} \text{d}(x,y)
+\end{equation}
+
+Note that for $x,y \in \mathcal{C}$, d$(x,y)=0$ for $x=y$, and $d \le$ d$(x,y)$ for $x\neq y$.  This implies that
+\begin{equation}
+M(M-1)d\le S
+\end{equation}
+
+This comes directly from equation \ref{plotkin_1}.
+We have $M$ possible codewords to consider for $x$ in the outer summation, $M-1$ distinct codewords from $x$ to consider in the inner summation for $y$, and the distance between $x$ and $y$ will always be greater than or equal to $d$.
+
+Next, let $\mathcal{M}$ be the $M \times n$ matrix whose rows are the codewords of $\mathcal{C}$.  For $1 \le i \le n$, let $n_{i,\alpha}$ be the number of times $\alpha \in
+ \mathbb{F}_q$ occurs in column $i$ of $\mathcal{M}$.  Note that $\sum_{\alpha \in \mathbb{F}_q} n_{i,\alpha} = M$ for $1\le i \le n$.  This is simply because there are $M$ total
+ elements of $\mathbb{F}_q$ in each column, so the sum over all $n_{i,\alpha}$ must necessarily be $M$.  Consequently, we have
+
+\begin{equation}
+\begin{split}
+S = \sum_{i=1}^{n} \sum_{\alpha\in\mathbb{F}_q} n_{i,\alpha}(M - n_{i,\alpha}) &= M\sum_{i=1}^{n} \sum_{\alpha\in\mathbb{F}_q} n_{i,\alpha} - \sum_{i=1}^{n} \sum_{\alpha\in\mathbb{F}_q} n_{i,\alpha}^2 \\
+&= nM^2 - \sum_{i=1}^{n} \sum_{\alpha\in\mathbb{F}_q} n_{i,\alpha}^2
+\end{split}
+\end{equation}
+
+Recall the Cauchy-Schwarz inequality, which states that 
+\begin{equation}
+\left(\sum_{i=1}^n x_i y_i \right )^2 \le \left(\sum_{i=1}^n x_i^2 \right ) \left(\sum_{i=1}^n y_i^2 \right )
+\end{equation}
+
+For our purposes, this means that 
+\begin{equation}
+\left(\sum_{\alpha\in\mathbb{F}_q} 1\cdot n_{i,\alpha} \right )^2 \le q \left(\sum_{\alpha\in\mathbb{F}_q} n_{i,\alpha}^2 \right )
+\end{equation}
+
+Using this inequality, we obtain
+
+\begin{equation}
+S \le nM^2 - \sum_{i=1}^n q^{-1} \left(\sum_{\alpha\in\mathbb{F}_q} 1\cdot n_{i,\alpha} \right )^2 = nM^2 - \frac{nM^2}{q} = nrM^2
+\end{equation}
+
+Combining the two, we get FINISH.
+
+\end{proof}
 
@@
 
-Plotkin
-talk about importance
-define it
-prove it
-work out some examples
-
 Elias
@@
 
-\end{comment}
-
 \end{document}

### 2015-04-16 draft.tex
added some plotkin examples

@@
 \newtheorem{theorem}{Theorem}
-\numberwithin{theorem}{subsection}
+%\numberwithin{theorem}{subsection}
+
+\theoremstyle{definition}
+\newtheorem{exmp}{Example}
+\numberwithin{exmp}{subsection}
 
@@
 
-The Plotkin Bound is an upper bound that often improves upon the Sphere Packing Bound on $A_q(n,d)$.  It is limited, however, in that it is only valid when $d$ is sufficiently
-close to $n$.  Consider that for $q=2$ our restriction is $n<2d$,  for $q=3$ our restriction is $n<\frac{3}{2}d$, for $q=4$ our restriction is $n<\frac{4}{3}d$, etc.  For large $q$, the
-number of codes we can consider becomes increasingly limited.
+The Plotkin Bound is an upper bound that often improves upon the Sphere Packing Bound on $A_q(n,d)$.
 
@@
 
+Before proving this bound, it is important to note that it is only valid when $d$ is sufficiently close to $n$.  For large $q$, this is can be a considerable limiting factor.
+Consider that for $q=2$ our restriction is $n<2d$,  for $q=3$ our restriction is $n<\frac{3}{2}d$, for $q=4$ our restriction is $n<\frac{4}{3}d$, etc.
+
 \begin{proof}
@@
 Note that for $x,y \in \mathcal{C}$, d$(x,y)=0$ for $x=y$, and $d \le$ d$(x,y)$ for $x\neq y$.  This implies that
-\begin{equation}
+\begin{equation} \label{plotkin_1_5}
 M(M-1)d\le S
@@
 This comes directly from equation \ref{plotkin_1}.
-We have $M$ possible codewords to consider for $x$ in the outer summation, $M-1$ distinct codewords from $x$ to consider in the inner summation for $y$, and the distance between $x$ and $y$ will always be greater than or equal to $d$.
+We have $M$ possible codewords to consider for $x$ in the outer summation, $M-1$ distinct codewords from $x$ to consider in the inner summation for $y$,
+and the distance between $x$ and $y$ will always be greater than or equal to the minimum distance $d$.
 
@@
  \mathbb{F}_q$ occurs in column $i$ of $\mathcal{M}$.  Note that $\sum_{\alpha \in \mathbb{F}_q} n_{i,\alpha} = M$ for $1\le i \le n$.  This is simply because there are $M$ total
- elements of $\mathbb{F}_q$ in each column, so the sum over all $n_{i,\alpha}$ must necessarily be $M$.  Consequently, we have
+ elements of $\mathbb{F}_q$ in each column, so the sum over all $n_{i,\alpha}$ must necessarily be $M$.
+
+I claim that we can rewrite $S$ as a double sum over these $n_{i,\alpha}$ values.  Specifically,
+
+\begin{equation}
+S = \sum_{i=1}^{n} \sum_{\alpha\in\mathbb{F}_q} n_{i,\alpha}(M - n_{i,\alpha}).
+\end{equation}
+
+Note that $n_{i,\alpha}(M - n_{i,\alpha})$ is multiplying the number of times $\alpha$ occurs in column $i$ by the number of times it doesn't occur in column $i$.
+In other words, we're counting the number of times two elements of the same
+column are not equivalent, exactly the condition that constitutes our Hamming distance.   By summing over all $\alpha$ and then all columns, we arrive at the same value generated by \ref{plotkin_1}.
+
+Next, simplify:
 
@@
 \begin{split}
-S = \sum_{i=1}^{n} \sum_{\alpha\in\mathbb{F}_q} n_{i,\alpha}(M - n_{i,\alpha}) &= M\sum_{i=1}^{n} \sum_{\alpha\in\mathbb{F}_q} n_{i,\alpha} - \sum_{i=1}^{n} \sum_{\alpha\in\mathbb{F}_q} n_{i,\alpha}^2 \\
+\sum_{i=1}^{n} \sum_{\alpha\in\mathbb{F}_q} n_{i,\alpha}(M - n_{i,\alpha}) &= M\sum_{i=1}^{n} \sum_{\alpha\in\mathbb{F}_q} n_{i,\alpha} - \sum_{i=1}^{n} \sum_{\alpha\in\mathbb{F}_q} n_{i,\alpha}^2 \\
 &= nM^2 - \sum_{i=1}^{n} \sum_{\alpha\in\mathbb{F}_q} n_{i,\alpha}^2
@@
 
-\begin{equation}
+\begin{equation} \label{plotkin_2}
 S \le nM^2 - \sum_{i=1}^n q^{-1} \left(\sum_{\alpha\in\mathbb{F}_q} 1\cdot n_{i,\alpha} \right )^2 = nM^2 - \frac{nM^2}{q} = nrM^2
@@
 
-Combining the two, we get FINISH.
+Combining \ref{plotkin_1_5} and \ref{plotkin_2}, we get
+
+\begin{equation}
+M(M-1)d \le nrM^2
+\end{equation}
+
+which simplifies to
+
+\begin{equation}
+M \le \left\lfloor \frac{d}{d-rn} \right\rfloor
+\end{equation}
 
 \end{proof}
+
+It is interesting to see exactly how the Sphere Packing and Plotkin bounds compare for specific values of $n$ and $d$.  For the following examples we will assume $q=2$.    
+Also, recall that if $d$ is even, $A_2(n,d) = A_2(n-1,d-1)$.
+
+\begin{exmp}
+$(n,d) = (7,4)$.
+
+Applying the Sphere Packing bound, we have $A_2(7,4) = A_2(6,3) \le \frac{2^6}{1 + 6}$, 
+giving us $A_2(7,4) \le 9$.
+
+Applying the Plotkin bound, we have $A_2(7,4) \le \frac{4}{4-\frac{1}{2}\cdot7} = 8$.
+
+\end{exmp}
+
+\begin{exmp}
+$(n,d) = (9,6)$.
+
+Applying Sphere Packing, we have  $A_2(9,6) = A_2(8,5) \le \frac{2^8}{1+8+28}$, giving us $A_2(n,d) \le 6$.
+
+Applying the Plotkin bound, we have $A_2(9,6) \le \frac{6}{6-\frac{1}{2}\cdot9} = 4$.
+\end{exmp}
 

### 2015-04-16 draft.tex
added plotkin.m, images there but broken

@@
 \usepackage{verbatim}
+\usepackage{graphicx}
+\usepackage{caption}
+\usepackage{subfig}
 
-%\usepackage{graphicx}
 %\usepackage{caption}
@@
 Before proving this bound, it is important to note that it is only valid when $d$ is sufficiently close to $n$.  For large $q$, this is can be a considerable limiting factor.
-Consider that for $q=2$ our restriction is $n<2d$,  for $q=3$ our restriction is $n<\frac{3}{2}d$, for $q=4$ our restriction is $n<\frac{4}{3}d$, etc.
+Consider that our restriction is $n<2d$ for $q=2$, $n<\frac{3}{2}d$ for $q=3$, $n<\frac{4}{3}d$ for for $q=4$, etc.
 
@@
 
-Recall the Cauchy-Schwarz inequality, which states that 
-\begin{equation}
-\left(\sum_{i=1}^n x_i y_i \right )^2 \le \left(\sum_{i=1}^n x_i^2 \right ) \left(\sum_{i=1}^n y_i^2 \right )
-\end{equation}
-
-For our purposes, this means that 
-\begin{equation}
-\left(\sum_{\alpha\in\mathbb{F}_q} 1\cdot n_{i,\alpha} \right )^2 \le q \left(\sum_{\alpha\in\mathbb{F}_q} n_{i,\alpha}^2 \right )
-\end{equation}
+Recall the Cauchy-Schwarz inequality, which states that $\left(\sum_{i=1}^n x_i y_i \right )^2 \le \left(\sum_{i=1}^n x_i^2 \right ) \left(\sum_{i=1}^n y_i^2 \right )$
+For our purposes, this means that $\left(\sum_{\alpha\in\mathbb{F}_q} 1\cdot n_{i,\alpha} \right )^2 \le q \left(\sum_{\alpha\in\mathbb{F}_q} n_{i,\alpha}^2 \right )$.
 
@@
 \begin{equation} \label{plotkin_2}
-S \le nM^2 - \sum_{i=1}^n q^{-1} \left(\sum_{\alpha\in\mathbb{F}_q} 1\cdot n_{i,\alpha} \right )^2 = nM^2 - \frac{nM^2}{q} = nrM^2
+S \le nM^2 - \sum_{i=1}^n q^{-1} \left(\sum_{\alpha\in\mathbb{F}_q} 1\cdot n_{i,\alpha} \right )^2 = nM^2 - \frac{nM^2}{q} = nrM^2.
 \end{equation}
 
-Combining \ref{plotkin_1_5} and \ref{plotkin_2}, we get
+Combining \ref{plotkin_1_5} and \ref{plotkin_2}, we get $M(M-1)d \le nrM^2$, which simplifies to
 
 \begin{equation}
-M(M-1)d \le nrM^2
-\end{equation}
-
-which simplifies to
-
-\begin{equation}
-M \le \left\lfloor \frac{d}{d-rn} \right\rfloor
+M \le \left\lfloor \frac{d}{d-rn} \right\rfloor.
 \end{equation}
@@
 Applying the Sphere Packing bound, we have $A_2(7,4) = A_2(6,3) \le \frac{2^6}{1 + 6}$, 
-giving us $A_2(7,4) \le 9$.
+giving us $A_2(7,4) \le \textbf{9}$.
 
-Applying the Plotkin bound, we have $A_2(7,4) \le \frac{4}{4-\frac{1}{2}\cdot7} = 8$.
+Applying the Plotkin bound, we have $A_2(7,4) \le \frac{4}{4-\frac{1}{2}\cdot7} = \textbf{8}$.
 
@@
 
-Applying Sphere Packing, we have  $A_2(9,6) = A_2(8,5) \le \frac{2^8}{1+8+28}$, giving us $A_2(n,d) \le 6$.
+Applying Sphere Packing, we have  $A_2(9,6) = A_2(8,5) \le \frac{2^8}{1+8+28}$, giving us $A_2(n,d) \le \textbf{6}$.
 
-Applying the Plotkin bound, we have $A_2(9,6) \le \frac{6}{6-\frac{1}{2}\cdot9} = 4$.
+Applying the Plotkin bound, we have $A_2(9,6) \le \frac{6}{6-\frac{1}{2}\cdot9} = \textbf{4}$.
 \end{exmp}
+
+It is also interesting to consider a more broader picture of what is going on here.  Below is a graph comparing rates of codes versus the Sphere Packing and Plotkin bounds
+that we can calculate for those values for different values of q.
+
+\begin{figure}
+\begin{subfigure}{.5\textwidth}
+  \centering
+  \includegraphics[width=.8\linewidth]{plotkin_q2.png}
+  \caption{1a}
+  \label{fig:sfig1}
+\end{subfigure}%
+\begin{subfigure}{.5\textwidth}
+  \centering
+  \includegraphics[width=.8\linewidth]{plotkin_q3.png}
+  \caption{1b}
+  \label{fig:sfig2}
+\end{subfigure}
+\caption{plots of....}
+\label{fig:fig}
+\end{figure}
 

### 2015-04-16 plotkin.m

@@ -1,0 +1,33 @@
+syms k;
+for q = 2:5
+    r = 1-1/q;
+    data_sp = zeros(100000,2);
+    data_plt = zeros(100000,2);
+    count_sp = 1;
+    count_plt = 1;
+    
+   for n = 8:25
+       for d=(floor(r*n)+1):n
+           t = floor((d-1)/2);
+           sp = (q^n)/symsum(nchoosek(n,k)*(q-1)^k,0,t);
+           data_sp(count_sp,1) = d/n;
+           data_sp(count_sp,2) = sp;
+           count_sp=count_sp+1;
+           
+           if (d>r*n)
+               pltkn = d/(d-r*n);
+               data_plt(count_plt,1) = d/n;
+               data_plt(count_plt,2) = pltkn;
+               count_plt=count_plt+1;
+           end
+       end
+   end
+   figure;
+   scatter(data_sp(1:count_sp,1),data_sp(1:count_sp,2),'g')
+   hold on
+   scatter(data_plt(1:count_plt,1),data_plt(1:count_plt,2),'b')
+   title(['q = ',num2str(q)])
+   legend('Sphere Packing','Plotkin','Location','southwest');
+   xlabel('Relative Distance (d/n)');
+   ylabel('Bound');
+end

### 2015-04-18 greismer.m
compared to greismer

@@ -1,0 +1,15 @@
+function [val] = greismer(n,q,d)
+k=1;
+val = q;
+syms a;
+while(1)
+   temp = symsum(ceil(d/(q^a)),0,k-1);
+   if n<temp
+       return;
+   else
+       val = q^k;
+       k=k+1;
+   end
+end
+
+end

### 2015-04-18 plotkin.m

@@ -1,8 +1,9 @@
 syms k;
 for q = 2:5
     r = 1-1/q;
-    data_sp = zeros(100000,2);
+    data_sp_gr = zeros(100000,3);
     data_plt = zeros(100000,2);
+ 
     count_sp = 1;
     count_plt = 1;
     
@@ -10,8 +11,10 @@ for q = 2:5
        for d=(floor(r*n)+1):n
            t = floor((d-1)/2);
            sp = (q^n)/symsum(nchoosek(n,k)*(q-1)^k,0,t);
-           data_sp(count_sp,1) = d/n;
-           data_sp(count_sp,2) = sp;
+           gr = greismer(n,q,d);
+           data_sp_gr(count_sp,1) = d/n;
+           data_sp_gr(count_sp,2) = sp;
+           data_sp_gr(count_sp,3) = gr;
            count_sp=count_sp+1;
            
            if (d>r*n)
@@ -22,12 +25,15 @@ for q = 2:5
            end
        end
    end
+   
    figure;
-   scatter(data_sp(1:count_sp,1),data_sp(1:count_sp,2),'g')
+   scatter(data_sp_gr(1:count_sp,1),data_sp_gr(1:count_sp,2),'g')
    hold on
    scatter(data_plt(1:count_plt,1),data_plt(1:count_plt,2),'b')
+   hold on
+   scatter(data_sp_gr(1:count_sp,1),data_sp_gr(1:count_sp,3),'r')
    title(['q = ',num2str(q)])
-   legend('Sphere Packing','Plotkin','Location','southwest');
+   legend('Sphere Packing','Plotkin','Greismer','Location','southwest');
    xlabel('Relative Distance (d/n)');
    ylabel('Bound');
 end

### 2015-04-18 pltkn_greismer.m

@@ -1,0 +1,34 @@
+syms k;
+for q = 2:5
+    r = 1-1/q;
+    data_sp = zeros(100000,2);
+    data_plt = zeros(100000,2);
+    count_sp = 1;
+    count_plt = 1;
+    
+   for n = 8:25
+       for d=(floor(r*n)+1):n
+           t = floor((d-1)/2);
+           sp = (q^n)/symsum(nchoosek(n,k)*(q-1)^k,0,t);
+           data_sp(count_sp,1) = d/n;
+           data_sp(count_sp,2) = sp;
+           count_sp=count_sp+1;
+           
+           if (d>r*n)
+               pltkn = d/(d-r*n);
+               data_plt(count_plt,1) = d/n;
+               data_plt(count_plt,2) = pltkn;
+               count_plt=count_plt+1;
+           end
+       end
+   end
+   
+   figure;
+   scatter(data_sp(1:count_sp,1),data_sp(1:count_sp,2),'g')
+   hold on
+   scatter(data_plt(1:count_plt,1),data_plt(1:count_plt,2),'b')
+   title(['q = ',num2str(q)])
+   legend('Sphere Packing','Plotkin','Location','southwest');
+   xlabel('Relative Distance (d/n)');
+   ylabel('Bound');
+end

### 2015-04-19 draft.tex
compared to greismer
getting there

@@
 \usepackage{subfig}
+\usepackage{enumitem}
 
@@
 \newtheorem{theorem}{Theorem}
-%\numberwithin{theorem}{subsection}
+\numberwithin{theorem}{subsection}
 
@@
 \numberwithin{exmp}{subsection}
+
+\theoremstyle{definition}
+\newtheorem{defn}{Definition}
+\numberwithin{defn}{subsection}
+
+\theoremstyle{definition}
+\newtheorem{claim}{Claim}
+\numberwithin{claim}{subsection}
 
@@
 \section{Introduction}
+
+\begin{comment}
+PLAN
+do elias, don't prove first lemma, prove second lemma and thm
+do given examples, draw graphs
+finish out examples of lexicodes
+add graphs to plotkin
+finish analysis of asymptotic singleton and plotkin
+\end{comment}
 
@@
 
+\begin{comment}
 \begin{figure}
@@
 \end{figure}
+\end{comment}
+
+\section{Lexicodes}
+We end our discussion on bounds with an interesting class of binary linear codes
+called lexicodes, short for lexicographic codes.  Lexicodes are linear and meet the Gilbert bound; we will discuss the former and prove the latter.  Note that we are 
+working in $\mathbb{F}_2$.
+
+We construct the lexicode $\mathcal{L}$ of length $n$ and minimum distance $d$ using a basic greedy algorithm as follows.  First, order all $n$-tuples in lexicographic order:
+$0\cdots000$, $0\cdots001$, $0\cdots010$, $0\cdots011$, $0\cdots100$, et cetera.  Put the zero vector $\mathbf{0}$ in $\mathcal{L}$.  Next, find the first vector $\mathbf{x}$
+of weight $d$ in the lexicographic ordering, and put it in $\mathcal{L}$.  Then, find the next vector in  the lexicographic ordering whose distance from each vector in $\mathcal{L}$ is 
+$d$ or more and add it to $\mathcal{L}$, repeating this process until you have used up your lexicographic list.
+
+The set $\mathcal{L}$ is a linear code of length $n$ and minimum distance $d$.  The set $\mathcal{L}$ also contains linear subcodes which are generated by the above algorithm,
+but stopping at the right spots.
+
+\begin{theorem}
+After constructing $\mathcal{L}$ as above, label the vectors $\mathbf{c}_0$, $\mathbf{c}_1,$ $\ldots$ in the order they were selected such that $\mathbf{c}_0$ is the $\mathbf{0}$ 
+vector.
+
+\begin{enumerate}
+\item $\mathcal{L}$ is a linear code and the vectors $\mathbf{c}_{2^i}$ are a basis of $\mathcal{L}$.  
+\item After $\mathbf{c}_{2^i}$ is chosen, the next $2^i -1$ vectors can be rewritten as $\mathbf{c}_1 + \mathbf{c}_{2^i}$, $\mathbf{c}_2 + \mathbf{c}_{2^i}$, $\ldots$, 
+$\mathbf{c}_{2^i -1} + \mathbf{c}_{2^i}$.
+\item Let $\mathcal{L}_i = \{\mathbf{c}_0,\mathbf{c}_1,\ldots,\mathbf{c}_{2^i -1}\}$.  Then $\mathcal{L}_i$ is an $[n,i,d]$ linear code.
+
+\end{enumerate}
+
+\end{theorem}
+
+Though I won't prove this, it is not difficult to see that $1.$ and $3.$ follow from $2.$    In $2.$, we are showing that all codewords in the lexicode are simply linear combinations of 
+the $c_{2^i}$ codewords, hence making the $c_{2^i}$ codewords a basis for the code.
+
+The codes $\mathcal{L}_i$ satisfy the inclusions $\mathcal{L}_1 \subset \mathcal{L}_2 \subset \cdots \subset \mathcal{L}_k = \mathcal{L}$, where $k$ is the dimension of 
+$\mathcal{L}$.  In general, this dimension value $k$ is not known until you have completed the construction as described above.
+
+\begin{exmp}
+Consider the codes $\mathcal{L}_i$ of length $5$ and minimum distance $2$.  First, we must construct the entire lexicode $\mathcal{L}$.  To do so, we enumerate
+all 32 vectors of $\mathbb{F}_2^5$ in lexicographic order: $00000$,$00001$,$00010$,$\ldots$,$11111$.  We find that $\mathcal{L} = \{00000, 00011,00101,00110,01001,
+01010,01100,01111,10001,10010,\\ 10100,10111,11000,11011,11101,11110\}$.  As a sanity check, note that $\left | \mathcal{L} \right | = 16$, a power of 2.  Consequently, we have
+$\mathcal{L}_1 = \{00000,00011\}$, $\mathcal{L}_2 = \{00000, 00011,00101,\\ 00110\}$, $\mathcal{L}_3 = \{00000, 00011,00101,00110,01001,01010,01100,01111\}$, and
+$\mathcal{L}_4 = \mathcal{L}$. We can check to make sure that each $\mathbf{c}_j$ is a linear combination of the $\mathbf{c}_{2^i}$s. Consider $\mathcal{L}_3$:
+
+\begin{enumerate}[start=0]
+\item $\mathbf{c}_0$ is the trivial linear combination.
+\item $\mathbf{c}_1 = \mathbf{c}_1$
+\item $\mathbf{c}_2 = \mathbf{c}_2$
+\item $\mathbf{c}_3 = \mathbf{c}_1 + \mathbf{c}_2$.  $00110 = 00011+ 00101$.
+\item $\mathbf{c}_4 = 1\cdot\mathbf{c}_4$
+\item $\mathbf{c}_5 = \mathbf{c}_1 + \mathbf{c}_4$. $01010 = 00011 + 01001$.
+\item $\mathbf{c}_6 = \mathbf{c}_2 + \mathbf{c}_4$. $011000 = 00101 + 01001$.
+\item $\mathbf{c}_7 = \mathbf{c}_3 + \mathbf{c}_4 = \mathbf{c}_1 + \mathbf{c}_2 + \mathbf{c}_4$. $01111 = 00011 + 00101+01001$.
+\end{enumerate}
+
+The same analysis applies for all $\mathcal{L}_i$s.
+
+\end{exmp}
+
+Note that the greedy algorithm we descibed in the beginning of the section requires a strictly lexigraphical ordering, or else the code that is produced will not necessarily
+be linear.  Again consider the case of $\mathbb{F}_2^5$, but instead of the lexigraphical ordering, shift every vector up one such that the ordering is identical except now the
+zero vector is at the bottom of the list.  If we run our algorithm on this ordering, we will clearly not choose the zero vector to be a part of $\mathcal{L}$ and hence 
+$\mathcal{L}$ will not be linear.
+
+Also, note that lexicodes meet one of the bound we discussed in lecture, the Gilbert bound.  Recall the Gilbert bound:
+
+\begin{equation}
+B_q(n,d) \ge \frac{q^n}{\sum_{i=0}^{d-1} \binom{n}{i}(q-1)^{i}}
+\end{equation}
+
+\begin{claim}
+Lexicodes meet the Gilbert bound.
+\end{claim}
+
+\begin{proof}
+Consider an arbitrary lexicode $\mathcal{L}$.  Recall our construction of $\mathcal{L}$ with vectors in $\mathbb{F}_q^n$, wherein we visit each vector in our ordering,
+and if it is distance $d$ or more to every current element in $\mathcal{L}$ then we add it to our set.  More importantly, if a vector is distance $d-1$ or less to any vector in
+$\mathcal{L}$, then it is not selected.  Since we scan over every possible vector in $\mathbb{F}_q^n$, this implies that all vectors in $\mathbb{F}_q^n$ are distance less than
+or equal to $d-1$ from any vector in $\mathcal{L}$, as if at any point of our algorithm we reached some $v \in \mathbb{F}_q^n$, $v \not\in \mathcal{L}$,  we would have then
+added it $\mathcal{L}$, a contradiction.  Hence the covering radius of $\mathcal{L}$ is $d-1$.
+
+Now, it is enough to show that any code $\mathcal{C}$ with covering radius $d-1$ or less meets the Gilbert bound.  Recall that the Gilbert bound can be thought of as a restatement of the 
+following fact: (number of spheres around codewords) $\cdot$ (number of vectors in each sphere) $\ge$ (number of vectors in $\mathbb{F}_q^n$).  Since our covering radius
+is $d-1$ or less, none of the spheres for our lexicodes will overlap, and thus there will be no double counting of vectors when counting up the vectors in each individual sphere.
+Hence, $\mathcal{C}$ meets the Gilbert bound.
+\end{proof}
 

### 2015-04-23 draft.tex
progress maybe

@@
 \numberwithin{theorem}{subsection}
+
+\newtheorem{lemma}{Lemma}
+\numberwithin{lemma}{subsection}
 
@@
 In other words, we're counting the number of times two elements of the same
-column are not equivalent, exactly the condition that constitutes our Hamming distance.   By summing over all $\alpha$ and then all columns, we arrive at the same value generated by \ref{plotkin_1}.
+column are not equivalent, exactly the condition that constitutes the Hamming distance.   By summing over all $\alpha$ and then all columns, we arrive at the same value generated by \ref{plotkin_1}.
 
@@
 
-It is also interesting to consider a more broader picture of what is going on here.  Below is a graph comparing rates of codes versus the Sphere Packing and Plotkin bounds
+Using MATLAB, I sought to visualize how the Plotkin and Sphere Packing bounds compare.  To do so, I plotted their values over $8\le n \le 25$, with $d>rn$.
+
+In order to turn my discrete 3d data into a smooth mesh surface, I needed a mechanism to smooth out my data.  My solution was to utilize Delaunay triangulation.
+
+It is also interesting to consider a broader picture of how Plotkin compares to Sphere Packing, Greismer, and other bounds we have considered in lecture.
+Below is a graph comparing rates of codes versus the Sphere Packing and Plotkin bounds
 that we can calculate for those values for different values of q.
@@
 
+\subsection{Elias Upper Bound}
+
+Another upper bound on $A_q(n,d)$ is due to Elias in 1960.  The Elias bound is generally weaker than other bounds we have discussed, but is important because of the asymptotic
+form of this bound that we will discuss towards the end of this paper.
+
+In order to prove the Elias bound, two lemmas are necessary.
+
+\begin{lemma}
+Let $\mathcal{C}$ be an $(n,K,d)$ code over $\mathbb{F}_q$ such that all codewaords have weights at most w, where $w \le rn$ with $r=1-q^{-1}$.  Then
+\begin{equation}
+d\le \frac{Kw}{K-1}\left(2- \frac{w}{rn}\right).
+\end{equation}
+\end{lemma}
+
+\begin{lemma}
+Suppose C is an (n,M,d) code over $\mathbb{F}_q$.  Then there is an $(n,M,d)$ code $\mathcal{C}'$ over $\mathbb{F}_q$ with an (n,K,d) subcode $\mathcal{A}$ containing
+only codewords of weight at most w such that $K \ge M V_q(n,w) / q^n$.
+\end{lemma}
+
+\begin{theorem}
+Let $r=  1-q^{-1}$.  Suppose that $w\le rn$ and $w^2 - 2rnw + rnd > 0$.  Then
+
+\begin{equation}
+A_q(n,d) \le \frac{rnd}{w^2 - 2rnw + rnd}\cdot \frac{q^n}{V_q(n,w)}.
+\end{equation}
+\end{theorem}
+
+We can work through a few examples to see how the Elias bound operates.
+
+\begin{exmp}
+$n=14$, $d=6$, $q=2$. 
+Recall from before that $A_2(n,d)=A_2(n-1,d-1)$ if $d$ is even.  We will again use this fact to find the best possible bound that this theorem can provide.
+
+ For $w=0$, 
+we get $A_2(13,5)\le \frac{.5\cdot13\cdot5}{.5\cdot13\cdot5}\cdot\frac{2^{13}}{V_q(13,0)} = 2^{13} = 8192$; similarly, $A_2(14,6) = 2^{14} = 16384$.
+
+ For $w=1$, 
+we get $A_2(13,5)\le \frac{.5\cdot13\cdot5}{1 - 2\cdot.5\cdot13 + .5\cdot13\cdot5}\cdot\frac{2^{13}}{V_q(13,1)} = \frac{32.5}{1-13+32.5}\cdot\frac{2^{13}}{1+13} = 927$;
+similarly $A_2(14,6)\le \frac{.5\cdot14\cdot6}{1 - 2\cdot.5\cdot14 + .5\cdot14\cdot6}\cdot\frac{2^{14}}{V_q(14,1)} = \frac{42}{1-14+42}\cdot\frac{2^{14}}{1+14} = 1581$;
+
+\end{exmp}
+
+\section{Asymptotic Bounds}
+We now wish to consider these $A_q(n,d)$ values as n goes to infinity.  To do so, we must more formally define two terms.
+
+In class, we have considered the \textit{rate} of a linear code, $k/n$, as one measure of the goodness of a code.  That is,
+the rate tells us how much information relative to redundancy that our codewords provide.  The concept of rate can be generalized
+to non-linear codes as well.  For a possibly nonlinear code over $\mathbb{F}_q$ with $M$ codewords, the \textit{rate} is defined to be $n^{-1} \log_q {M}$.  Notice that
+for an $[n,k,d]$ linear code, $M = q^k$ and hence the rate is $k/n$ as we expect.
+
+A second notion of goodness that we have discussed, but I think not formally defined, is the \textit{relative distance} of a code.  For a linear or nonlinear code of length n
+has minimum distance d, this value is the ratio $d/n$.
+
+Consequently, for our asymptotic bounds, we are interested in the largest
+possible rate for a family of codes over $\mathbb{F}_q$ of lengths going to
+infinity with a relative distance of some constant $\delta$.  In other words, we consider the equation:
+
+\begin{equation}
+\alpha_{q}(\delta) = \limsup_{n \to \infty} n^{-1} \log_q A_q(n,\delta n)
+\end{equation}
+
+To better understand what is going on here, consider the case of an $[n,k,d]$ linear code $\mathcal{C}$.  Before, we wanted to know how large we could get $k$ given
+$n$ and $d$.  Now, we want to know how large we can get $\frac{k}{n}$ given $\frac{d}{n}=\delta$ as $n\to\infty$.  This idea generalizes to non-linear codes as 
+in the non-asymptotic cases we discussed in class.
+
+For the rest of this section, we will consider some bounds on $A_q(n,\delta n)$
+
+\subsection{Asymptotic Singleton Bound}
+
+Recall the Singleton Bound from lecture:
+
+\begin{theorem}
+For $d \le n$, $A_q(n,d) \le q^{n-d+1}$.
+\end{theorem}
+
+The asymptotic bound follows almost directly from the non-asymptotic variation.
+
+\begin{theorem}
+If $0 \le \delta \le 1$, then $\alpha_q(\delta) \le 1 - \delta$.
+\end{theorem}
+
+\begin{proof}
+\begin{equation} 
+\begin{split}
+\alpha_{q}(\delta) & = \limsup_{n \to \infty} n^{-1} \log_q A_q(n,\delta n) \\
+& \le \limsup_{n \to \infty} n^{-1} \log_q q^{n-\delta n+1} \\
+& \le \limsup_{n \to \infty} \frac{n-\delta n+1}{n} \\
+& \le 1 - \delta
+\end{split}
+\end{equation}
+\end{proof}
+
+\begin{exmp}
+
+\end{exmp}
+
+\subsection{Asymptotic Plotkin Bound}
+
 \section{Lexicodes}
 We end our discussion on bounds with an interesting class of binary linear codes
-called lexicodes, short for lexicographic codes.  Lexicodes are linear and meet the Gilbert bound; we will discuss the former and prove the latter.  Note that we are 
-working in $\mathbb{F}_2$.
+called lexicodes, short for lexicographic codes.  Lexicodes are linear and meet the Gilbert bound; we will discuss the former and prove the latter.  Note that for this discussion we are 
+solely working in $\mathbb{F}_2$.
 
-We construct the lexicode $\mathcal{L}$ of length $n$ and minimum distance $d$ using a basic greedy algorithm as follows.  First, order all $n$-tuples in lexicographic order:
-$0\cdots000$, $0\cdots001$, $0\cdots010$, $0\cdots011$, $0\cdots100$, et cetera.  Put the zero vector $\mathbf{0}$ in $\mathcal{L}$.  Next, find the first vector $\mathbf{x}$
-of weight $d$ in the lexicographic ordering, and put it in $\mathcal{L}$.  Then, find the next vector in  the lexicographic ordering whose distance from each vector in $\mathcal{L}$ is 
-$d$ or more and add it to $\mathcal{L}$, repeating this process until you have used up your lexicographic list.
+We construct the lexicode $\mathcal{L}$ of length $n$ and minimum distance $d$ using a basic greedy algorithm as follows.  First, order all $n$-tuples in an array $A$ in lexicographic order:
+$A[0] = 0\cdots000$, $A[1]=0\cdots001$, $A[2]0\cdots010$, $A[3]=0\cdots011$, \ldots, $A[2^n-1] = 1\cdots111$.
+Put the first vector from  $A$ (always the $\mathbf{0}$ vector) in $\mathcal{L}$.
+Next, find the first vector $\mathbf{x}$
+of weight $d$ in the lexicographic ordering, and put it in $\mathcal{L}$.  Then, find the next vector in the lexicographic ordering in $A$ whose distance from each vector in $\mathcal{L}$ is 
+$d$ or more and add it to $\mathcal{L}$.  Repeat this process until you have scanned through all of $A$ once.
 
@@
 all 32 vectors of $\mathbb{F}_2^5$ in lexicographic order: $00000$,$00001$,$00010$,$\ldots$,$11111$.  We find that $\mathcal{L} = \{00000, 00011,00101,00110,01001,
-01010,01100,01111,10001,10010,\\ 10100,10111,11000,11011,11101,11110\}$.  As a sanity check, note that $\left | \mathcal{L} \right | = 16$, a power of 2.  Consequently, we have
+01010,01100,01111,10001,10010,\\ 10100,10111,11000,11011,11101,11110\}$.  As a sanity check, note that $\left | \mathcal{L} \right | = 16$, a power of $q$.  Consequently, we have
 $\mathcal{L}_1 = \{00000,00011\}$, $\mathcal{L}_2 = \{00000, 00011,00101,\\ 00110\}$, $\mathcal{L}_3 = \{00000, 00011,00101,00110,01001,01010,01100,01111\}$, and
-$\mathcal{L}_4 = \mathcal{L}$. We can check to make sure that each $\mathbf{c}_j$ is a linear combination of the $\mathbf{c}_{2^i}$s. Consider $\mathcal{L}_3$:
+$\mathcal{L}_4 = \mathcal{L}$. We can check to make sure that each $\mathbf{c}_j$ is a linear combination of the $\mathbf{c}_{2^i}$s. For this example, consider $\mathcal{L}_3$:
+
+Notice that this is simply the even weight vectors.  In fact, it is true that for any $q$
+
+THIS IS THE EVEN WEIGHT CODE! prove it.
 
@@
 Note that the greedy algorithm we descibed in the beginning of the section requires a strictly lexigraphical ordering, or else the code that is produced will not necessarily
-be linear.  Again consider the case of $\mathbb{F}_2^5$, but instead of the lexigraphical ordering, shift every vector up one such that the ordering is identical except now the
+be linear.  Again consider the case of $\mathbb{F}_2^5$, but instead of the lexigraphical ordering, shift every vector up one such that the ordering is identical to before, except now the
 zero vector is at the bottom of the list.  If we run our algorithm on this ordering, we will clearly not choose the zero vector to be a part of $\mathcal{L}$ and hence 
@@
 Consider an arbitrary lexicode $\mathcal{L}$.  Recall our construction of $\mathcal{L}$ with vectors in $\mathbb{F}_q^n$, wherein we visit each vector in our ordering,
-and if it is distance $d$ or more to every current element in $\mathcal{L}$ then we add it to our set.  More importantly, if a vector is distance $d-1$ or less to any vector in
-$\mathcal{L}$, then it is not selected.  Since we scan over every possible vector in $\mathbb{F}_q^n$, this implies that all vectors in $\mathbb{F}_q^n$ are distance less than
-or equal to $d-1$ from any vector in $\mathcal{L}$, as if at any point of our algorithm we reached some $v \in \mathbb{F}_q^n$, $v \not\in \mathcal{L}$,  we would have then
-added it $\mathcal{L}$, a contradiction.  Hence the covering radius of $\mathcal{L}$ is $d-1$.
+and if it is distance $d$ or more to every current element in $\mathcal{L}$ then we add it to our set.  At the same time, notice that when a vector is visited in our algorithm, 
+if it has distance $d-1$ or less to any vector in $\mathcal{L}$, then it is not placed in $\mathcal{L}$.  Since all vectors in $\mathbb{F}_q^n$ are visited in our algorithm, any
+$v \in \mathbb{F}_q^n$ must either be in $\mathcal{L}$ or must have distance $d-1$ or less to some vector in $\mathcal{L}$.  Hence the covering radius of $\mathcal{L}$ is $d-1$.
 
-Now, it is enough to show that any code $\mathcal{C}$ with covering radius $d-1$ or less meets the Gilbert bound.  Recall that the Gilbert bound can be thought of as a restatement of the 
-following fact: (number of spheres around codewords) $\cdot$ (number of vectors in each sphere) $\ge$ (number of vectors in $\mathbb{F}_q^n$).  Since our covering radius
-is $d-1$ or less, none of the spheres for our lexicodes will overlap, and thus there will be no double counting of vectors when counting up the vectors in each individual sphere.
+Consequently, it is enough to show that any code $\mathcal{C}$ with covering radius $d-1$ or less meets the Gilbert bound.  Recall that the Gilbert bound can be thought of as a restatement of the 
+following fact: (number of spheres) $\cdot$ (number of vectors in a sphere with radius $d-1$) $\ge$ (number of vectors in $\mathbb{F}_q^n$).  Since our covering radius
+is $d-1$ or less, and we have that all codewords are distance $d$ or more apart, consequently no sphere of radius $d-1$ in $\mathbb{F}_q^n$ can contain more than one codeword.
+As a result, 
 Hence, $\mathcal{C}$ meets the Gilbert bound.
@@
 
-\section{Asymptotic Bounds}
-We now wish to consider these $A_q(n,d)$ values as n goes to infinity.  To do so, we must more formally define two terms.
+Some notable codes we have discussed in class are in fact lexicodes. For example, the binary lexicodes with $d$=3 and $n=2^m-1$ are the binary hamming codes.  It can be quite
+tedious to compute and confirm something like this by hand, so I wrote a short C++ program that implements the Lexicode algorithm as described above.
 
-In class, we have considered the \textit{rate} of a linear code, $k/n$, as one measure of the goodness of a code.  That is,
-the rate tells us how much information relative to redundancy that our codewords provide.  The concept of rate can be generalized
-to non-linear codes as well.  For a possibly nonlinear code over $\mathbb{F}_q$ with $M$ codewords, the \textit{rate} is defined to be $n^{-1} \log_q {M}$.  Notice that
-for an $[n,k,d]$ linear code, $M = q^k$ and hence the rate is $k/n$ as we expect.
+\begin{exmp}
+Let $n=7$, $d=3$.  We find $\mathcal{L}= \{0000000,000111,  \}$
+\end{exmp}
 
-A second notion of goodness that we have discussed, but I think not formally defined, is the \textit{relative distance} of a code.  For a linear or nonlinear code of length n
-has minimum distance d, this value is the ratio $d/n$.
-
-Consequently, for our asymptotic bounds, we are interested in the largest possible rate for a family of codes over $\mathbb{F}_q$ of lengths going to infinity with relative 
-distances approaching some constant $\delta$.  In other words, we consider the equation:
-
-\begin{equation}
-\alpha_{q}(\delta) = \limsup_{n \to \infty} n^{-1} \log_q A_q(n,\delta n)
-\end{equation}
-
-[What does this imply?]
-
-\subsection{Asymptotic Singleton Bound}
-
-Recall the Singleton Bound from lecture:
-
-\begin{theorem}
-For $d \le n$, $A_q(n,d) \le q^{n-d+1}$.
-\end{theorem}
-
-[explain what this means, what are the implications]
-
-\begin{theorem}
-If $0 \le \delta \le 1$, then $\alpha_q(\delta) \le 1 - \delta$.
-\end{theorem} 
-This theorem follows directly from the Singleton bound.
-
-\begin{proof}
-\begin{equation} 
-\begin{split}
-\alpha_{q}(\delta) & = \limsup_{n \to \infty} n^{-1} \log_q A_q(n,\delta n) \\
-& \le \limsup_{n \to \infty} n^{-1} \log_q q^{n-\delta n+1} \\
-& \le \limsup_{n \to \infty} \frac{n-\delta n+1}{n} \\
-& \le 1 - \delta
-\end{split}
-\end{equation}
-\end{proof}
-
-\subsection{Asymptotic Plotkin Bound}
+Need to talk about paper
+http://ieeexplore.ieee.org/stamp/stamp.jsp?arnumber=1057187
 

### 2015-04-23 hamming.cpp

@@ -1,0 +1,50 @@
+#include <iostream>
+#include <cstdint>
+
+using namespace std;
+
+int popcount_1(uint64_t x);
+uint wegner(uint input);
+
+const uint64_t m1  = 0x5555555555555555; //binary: 0101...
+const uint64_t m2  = 0x3333333333333333; //binary: 00110011..
+const uint64_t m4  = 0x0f0f0f0f0f0f0f0f; //binary:  4 zeros,  4 ones ...
+const uint64_t m8  = 0x00ff00ff00ff00ff; //binary:  8 zeros,  8 ones ...
+const uint64_t m16 = 0x0000ffff0000ffff; //binary: 16 zeros, 16 ones ...
+const uint64_t m32 = 0x00000000ffffffff; //binary: 32 zeros, 32 ones
+const uint64_t hff = 0xffffffffffffffff; //binary: all ones
+const uint64_t h01 = 0x0101010101010101; //the sum of 256 to the power of 0,1,2,3...
+
+
+
+int main(){
+	uint64_t x;
+	while(1){
+		cin >> x;
+		cout << popcount_1(x) << endl;
+		cout << wegner(x) << endl;
+	}
+	
+	return 0;
+}
+
+
+int popcount_1(uint64_t x) {
+    x = (x & m1 ) + ((x >>  1) & m1 ); //put count of each  2 bits into those  2 bits 
+    x = (x & m2 ) + ((x >>  2) & m2 ); //put count of each  4 bits into those  4 bits 
+    x = (x & m4 ) + ((x >>  4) & m4 ); //put count of each  8 bits into those  8 bits 
+    x = (x & m8 ) + ((x >>  8) & m8 ); //put count of each 16 bits into those 16 bits 
+    x = (x & m16) + ((x >> 16) & m16); //put count of each 32 bits into those 32 bits 
+    x = (x & m32) + ((x >> 32) & m32); //put count of each 64 bits into those 64 bits 
+    return x;
+}
+
+uint wegner(uint input)
+        {
+            uint count;
+            for (count = 0; input!=0; count++)
+            {
+                input &= input - 1; // turn off the rightmost 1-bit
+            }
+            return count;
+        }

### 2015-04-23 plotkin_solo.m

@@ -1,0 +1,40 @@
+syms k;
+for q = 2:5
+    r = 1-1/q;
+    %data_sp_gr = zeros(100000,3);
+    data_plt = zeros(100000,3);
+ 
+    %count_sp = 1;
+    count_plt = 1;
+    
+   for n = 8:25
+       for d=(floor(r*n)+1):n
+           t = floor((d-1)/2);
+           %sp = (q^n)/symsum(nchoosek(n,k)*(q-1)^k,0,t);
+           %count_sp=count_sp+1;
+           
+           pltkn = d/(d-r*n);
+           data_plt(count_plt,1) = n;
+           data_plt(count_plt,2) = d;
+           data_plt(count_plt,3) = pltkn;
+           count_plt=count_plt+1;
+       end
+   end
+    
+   tri = delaunay(data_plt(1:count_plt,1),data_plt(1:count_plt,2));
+   
+   figure;
+   trisurf(tri,data_plt(1:count_plt,1),data_plt(1:count_plt,2),data_plt(1:count_plt,3));
+   axis vis3d
+   
+%    figure;
+%    scatter(data_sp_gr(1:count_sp,1),data_sp_gr(1:count_sp,2),'g')
+%    hold on
+%    scatter(data_plt(1:count_plt,1),data_plt(1:count_plt,2),'b')
+%    hold on
+%    scatter(data_sp_gr(1:count_sp,1),data_sp_gr(1:count_sp,3),'r')
+%    title(['q = ',num2str(q)])
+%    legend('Sphere Packing','Plotkin','Greismer','Location','southwest');
+%    xlabel('Relative Distance (d/n)');
+%    ylabel('Bound');
+end

### 2015-04-23 sphere_packing_solo.m

@@ -1,0 +1,39 @@
+syms k;
+for q = 2:5
+    r = 1-1/q;
+    %data_sp_gr = zeros(100000,3);
+    data_plt = zeros(100000,3);
+ 
+    %count_sp = 1;
+    count_plt = 1;
+    
+   for n = 8:25
+       for d=n/2:n
+           t = floor((d-1)/2);
+           sp = (q^n)/symsum(nchoosek(n,k)*(q-1)^k,0,t);
+           
+           pltkn = d/(d-r*n);
+           data_plt(count_plt,1) = n;
+           data_plt(count_plt,2) = d;
+           data_plt(count_plt,3) = sp;
+           count_plt=count_plt+1;
+       end
+   end
+    
+   tri = delaunay(data_plt(1:count_plt,1),data_plt(1:count_plt,2));
+   
+   figure;
+   trisurf(tri,data_plt(1:count_plt,1),data_plt(1:count_plt,2),data_plt(1:count_plt,3));
+   axis vis3d
+   
+%    figure;
+%    scatter(data_sp_gr(1:count_sp,1),data_sp_gr(1:count_sp,2),'g')
+%    hold on
+%    scatter(data_plt(1:count_plt,1),data_plt(1:count_plt,2),'b')
+%    hold on
+%    scatter(data_sp_gr(1:count_sp,1),data_sp_gr(1:count_sp,3),'r')
+%    title(['q = ',num2str(q)])
+%    legend('Sphere Packing','Plotkin','Greismer','Location','southwest');
+%    xlabel('Relative Distance (d/n)');
+%    ylabel('Bound');
+end

### 2015-04-23 draft.tex
started new lexicode proof

@@
 \usepackage{graphicx}
-\usepackage{caption}
-\usepackage{subfig}
-\usepackage{enumitem}
+%\usepackage{caption}
+%\usepackage{subfig}
+%\usepackage{enumitem}
 
@@
 
-Notice that this is simply the even weight vectors.  In fact, it is true that for any $q$
-
+Notice that this is simply the even weight vectors.  In fact, it is true that
+for any $q$.
 THIS IS THE EVEN WEIGHT CODE! prove it.
 
-\begin{enumerate}[start=0]
+\begin{enumerate}%[start=0]
 \item $\mathbf{c}_0$ is the trivial linear combination.
@@
 is $d-1$ or less, and we have that all codewords are distance $d$ or more apart, consequently no sphere of radius $d-1$ in $\mathbb{F}_q^n$ can contain more than one codeword.
-As a result, 
+Our spheres will still overlap, however, meaning (number of vectors in
+$\mathbb{F}_q^n$)/(number of vectors in a sphere with radius $d-1$) will
+certainly be greater than or equal to the number of spheres around codewords.
 Hence, $\mathcal{C}$ meets the Gilbert bound.
@@
 
-Some notable codes we have discussed in class are in fact lexicodes. For example, the binary lexicodes with $d$=3 and $n=2^m-1$ are the binary hamming codes.  It can be quite
+Some notable codes we have discussed in class are in fact lexicodes.
+[REFERENCE]
+
+We can prove a basic property of binary Lexicodes.  First, though, we
+need an important definition.
+
+\begin{defn}
+The $\mathbf{nim-sum}$ NS($v$) of a vector $v \in \mathbb{F}_2^n$ is the sum of
+it's coordinates in GF($2$).
+\end{defn}
+
+\begin{defn}
+A vector $v\in \mathbb{F}_2^n$ is $\mathbf{zero-sum}$ if NS($v$)=0.
+\end{defn}
+
+We have used the idea of nim-sums and zero-sums throughout the course, but instead we have
+referred to this notion in terms being even-like or odd-like.  This is the
+exact same notion, only in different terms.
+
+\begin{claim}
+For $d=q=2$, $\forall v\in \mathcal{L}$, NS($v$) $= 0$, and hence $\mathcal{L}$ is an even-like code.
+\end{claim}
+
+\begin{proof}
+We will prove this by inducting on $n$.  In the base case of $n=1$,
+$\mathcal{L}=\{0\}$, which is trivially zero-sum.  Assume that for the
+lexicode of length $n$, which we will denote $\mathcal{L}(n)$, all codewords are zero-sum.  Now, we must show that all
+the codewords in $\mathcal{L}(n+1)$ are zero-sum as well.  First, note that all
+codewords in $\mathcal{L}(n)$ are also in $\mathcal{L}(n+1)$, except with an
+extra leading zero.  By our assumption, these codewords are still zero-sum, as
+adding a zero in front will not change the nim-sum calculation.
+Now, we must show that any vector we can add to this set as proscribed by our
+algorithm must necessarily be a zero-sum vector as well.
+\end{proof}
+
+For example, the binary lexicodes with $d$=3 and $n=2^m-1$ are the binary hamming codes.  It can be quite
 tedious to compute and confirm something like this by hand, so I wrote a short C++ program that implements the Lexicode algorithm as described above.

### 2015-04-24 draft.tex
figured out lexicode proof

@@
 We have used the idea of nim-sums and zero-sums throughout the course, but instead we have
-referred to this notion in terms being even-like or odd-like.  This is the
+referred to this notion in terms of being even-like or odd-like.  This is the
 exact same notion, only in different terms.
@@
 adding a zero in front will not change the nim-sum calculation.
-Now, we must show that any vector we can add to this set as proscribed by our
+Now, we must show that any vector we can add to this set as prescribed by our
 algorithm must necessarily be a zero-sum vector as well.
+
+Since $\mathcal{L}(n)$ is contained in $\mathcal{L}(n+1)$, we begin our construction of $\mathcal{L}(n+1)$ with the elements of $\mathcal{L}(n)$.  Any new elements
+we will add must have a $1$ in the leading coordinate as we have maxed out our possibilities for $\mathcal{L}(n)$, and so lexicographically this makes sense as the new vectors we now need to consider will be `larger' than the ones
+we have already added in to $\mathcal{L}(n+1)$.
+
+-If you approach an odd-weight vector that you can add, then there is even-weight vector that comes one before it that you should have added instead.
+
+-SHIT! if it is odd weight, then by definition that means that has a 1 in the leading column plus an even weight vector from $\mathcal{L}(n)$!!!!  That vector must necessarily be 
+distance 1 away from a vector in $\mathcal{L}(n)$, and thus cannot be added to $\mathcal{L}(n+1)$.  All even weight vectors will have a $1$ in the leading coordinate and then
+an odd number of $1$s in the next $n$ coordinates.  No odd numbers are in $\mathcal{L}(n)$, and so you will be at least distance one from all vectors already from $\mathcal{L}(n)$.
+So you get one component of your distance from the leading coordinate and at least one component of distance from you the last $n$ coordinates.  This completes the 
+proof!
 \end{proof}

### 2015-04-26 draft.tex
draft finished, revise and then submit

--- 2015-04-23 draft.tex
@@
 \usepackage{graphicx}
+\usepackage{enumerate}
+%\usepackage{figure}
+
 %\usepackage{caption}
@@
 
-\newtheorem{theorem}{Theorem}
-\numberwithin{theorem}{subsection}
-
-\newtheorem{lemma}{Lemma}
-\numberwithin{lemma}{subsection}
-
+\theoremstyle{plain}
+  \newtheorem{theorem}{Theorem}[section]
+  \newtheorem{prop}[theorem]{Proposition}
+  \newtheorem{cor}[theorem]{Corollary}
+  \newtheorem{lemma}[theorem]{Lemma}
+  \newtheorem{claim}[theorem]{Claim}
 \theoremstyle{definition}
-\newtheorem{exmp}{Example}
-\numberwithin{exmp}{subsection}
-
-\theoremstyle{definition}
-\newtheorem{defn}{Definition}
-\numberwithin{defn}{subsection}
-
-\theoremstyle{definition}
-\newtheorem{claim}{Claim}
-\numberwithin{claim}{subsection}
+  \newtheorem{defn}[theorem]{Definition}
+  \newtheorem{exmp}[theorem]{Example}
+  \newtheorem{obs}[theorem]{Observation}
+  \newtheorem{remark}[theorem]{Remark}
+  \newtheorem{construction}[theorem]{Construction}
 
@@
 In the first part of the paper, we will consider the Plotkin Upper bound, 
-the Elias Upper bound, and the Linear Programming Upper Bound.  In the second part of the paper, we will consider asymptotic versions
-of Singleton, Plotkin, Hamming, and Elias.  (I am very certain that I won't get to discuss all of these bounds, but I am currently unsure how much space each discussion will take up so I've
-listed all that I am considering.)  For each bound, we will consider its proof as well
-as related examples.  Lastly, in the final part we will consider lexicodes, an interesting subset of linear codes that meet the Gilbert Bound.
-
-Some implementation specific details: for the Linear Programming bound, I will introduce basic linear programming concepts and as well as the Krawtchouck polynomials.  For the 
-Asymptotic Hamming bound I will introduce the Hilbert entropy function.
+the Elias Upper bound.
+In the second part of the paper, we will consider the asymptotic versions of the Singleton, Plotkin, and Elias bounds.
+Lastly, in the final part we will consider lexicodes, an interesting subset of linear codes that meet the Gilbert Bound.
 
@@
 \subsection{Plotkin Upper Bound}
-%Plotkin
-%talk about importance
-%define it
-%prove it
-%work out some examples
 
@@
 
-Using MATLAB, I sought to visualize how the Plotkin and Sphere Packing bounds compare.  To do so, I plotted their values over $8\le n \le 25$, with $d>rn$.
+Using MATLAB, I sought to visualize how the Plotkin and Sphere Packing bounds compare.  To do so, I plotted their values over $8\le n \le 25$, with $d>rn$.  Below is the case
+of $q=2$; I found similar but more smoothed out results for higher values of $q$ (see submission folder).
 
-In order to turn my discrete 3d data into a smooth mesh surface, I needed a mechanism to smooth out my data.  My solution was to utilize Delaunay triangulation.
+\begin{figure}[ht]
+\includegraphics[width=.8\linewidth]{plotkin_q2.png}
+\caption{Plotkin and Sphere Packing bounds for $n,d\in[8,25]$}
+\end{figure}
+I also thought it would be interesting to visualize how the Plotkin bound and Sphere Packing bounds operate as a function of $n$ and $d$.
+Given various values of $n$ and $d$, I plotted the resulting bound,
+and then used Delaunay triangulation [REFERENCE] to turn the discrete 3D data into a smooth mesh surface.  (See Sphere Packing data on next page).
 
-It is also interesting to consider a broader picture of how Plotkin compares to Sphere Packing, Greismer, and other bounds we have considered in lecture.
-Below is a graph comparing rates of codes versus the Sphere Packing and Plotkin bounds
-that we can calculate for those values for different values of q.
+\begin{figure}
+\centering
+\begin{minipage}[b]{0.45\linewidth}
+\includegraphics[width=1.4\linewidth]{plotkin.png}
+\label{fig:minipage1}
+\end{minipage}
+\quad
+\begin{minipage}[b]{0.45\linewidth}
+\includegraphics[width=1.4\linewidth]{plotkin_2.png}
+\label{fig:minipage2}
+\end{minipage}
+\caption{Two different perspectives of the same graph, the Plotkin Bound for $q$=2, $n,d\in[6,40]$ }
+\end{figure}
 
-\begin{comment}
 \begin{figure}
-\begin{subfigure}{.5\textwidth}
 \centering
-  \includegraphics[width=.8\linewidth]{plotkin_q2.png}
-  \caption{1a}
-  \label{fig:sfig1}
-\end{subfigure}%
-\begin{subfigure}{.5\textwidth}
-  \centering
-  \includegraphics[width=.8\linewidth]{plotkin_q3.png}
-  \caption{1b}
-  \label{fig:sfig2}
-\end{subfigure}
-\caption{plots of....}
-\label{fig:fig}
+\begin{minipage}[ht]{0.45\linewidth}
+\includegraphics[width=1.4\linewidth]{sp_1.png}
+\label{fig:minipage1}
+\end{minipage}
+\quad
+\begin{minipage}[ht]{0.45\linewidth}
+\includegraphics[width=1.4\linewidth]{sp_2.png}
+\label{fig:minipage2}
+\end{minipage}
+\caption{Two different perspectives of the same graph, the Sphere Packing Bound for $q$=2, $n,d\in[6,40]$ }
 \end{figure}
-\end{comment}
 
@@
 Another upper bound on $A_q(n,d)$ is due to Elias in 1960.  The Elias bound is generally weaker than other bounds we have discussed, but is important because of the asymptotic
-form of this bound that we will discuss towards the end of this paper.
+form that it generates.
 
@@
 
+The proof of this lemma uses a very similar technique to that used in our proof of the Plotkin bound. Just as before, given an $(n,K,d)$ code $\mathcal{C}$, the proof considers
+the $K \times n$ matrix $\mathcal{M}$ whose rows are the codewords of $\mathcal{C}$.  Using this matrix, the proof takes the expression $K(K-1)d$ and shows through a number of equation manipulations
+that it is less than or equal the expression $K^2 w\left( 2 - \frac{w}{rn}\right )$.  Two key tools for the proof are the Cauchy-Schwartz inequality, and the relationship between 
+the sum of the distances between all pairwise codewords and the sums of the $n_{i,\alpha}$ values in the columns of $\mathcal{M}$.
+
+As an aside: the second lemma, stated below, uses the notation $V_q(n,a)$ to denote the number of vectors in a sphere of radius $a$ in $\mathbb{F}_q^n$.  This is a concept 
+that we became very familiar with this semester in our discussions of the Sphere Packing and Gilbert bounds.
+
 \begin{lemma}
@@
 \end{lemma}
+
+The proof of this lemma begins by considering the intersection between a sphere of radius w centered at $\mathbf{0}$, and the special vector $x\in \mathbb{F}_q^n$ added to $\mathcal{C}$ such that the intersection
+is maximal.  The important step is noticing that this value is greater than or equal to the sum over all vectors $y\in\mathbb{F}_q^n$ of that same sphere of radius $w$, intersected with 
+$y+\mathcal{C}$, all divided by $q^n$.  The proof then uses sum manipulations to find a relationship between our original expression and $\frac{1}{q^n}V_q(n,w)M$.
 
@@
 \end{theorem}
+
+The proof of this theorem, though omitted, follows almost directly from the previous two lemmas.
 
@@
 we get $A_2(13,5)\le \frac{.5\cdot13\cdot5}{1 - 2\cdot.5\cdot13 + .5\cdot13\cdot5}\cdot\frac{2^{13}}{V_q(13,1)} = \frac{32.5}{1-13+32.5}\cdot\frac{2^{13}}{1+13} = 927$;
-similarly $A_2(14,6)\le \frac{.5\cdot14\cdot6}{1 - 2\cdot.5\cdot14 + .5\cdot14\cdot6}\cdot\frac{2^{14}}{V_q(14,1)} = \frac{42}{1-14+42}\cdot\frac{2^{14}}{1+14} = 1581$;
+similarly $A_2(14,6)\le \frac{.5\cdot14\cdot6}{1 - 2\cdot.5\cdot14 + .5\cdot14\cdot6}\cdot\frac{2^{14}}{V_q(14,1)} = \frac{42}{1-14+42}\cdot\frac{2^{14}}{1+14} = 1581$.
+
+For $w=2$, 
+we get  $A_2(13,5)\le \frac{.5\cdot13\cdot5}{4 - 2\cdot2\cdot.5\cdot13 + .5\cdot13\cdot5}\cdot\frac{2^{13}}{V_q(13,2)} = \frac{32.5}{4-26+32.5}\cdot\frac{2^{13}}{1+13+78} = 275$;
+similarly $A_2(14,6)\le \frac{.5\cdot14\cdot6}{4 - 2\cdot2\cdot.5\cdot14 + .5\cdot14\cdot6}\cdot\frac{2^{14}}{V_q(14,2)} = \frac{42}{4-28+42}\cdot\frac{2^{14}}{1+14+91} = 360$.
+
+For $w=3$, 
+we get  $A_2(13,5)\le \frac{.5\cdot13\cdot5}{9 - 2\cdot3\cdot.5\cdot13 + .5\cdot13\cdot5}\cdot\frac{2^{13}}{V_q(13,3)} = \frac{32.5}{9-39+32.5}\cdot\frac{2^{13}}{1+13+78+286} = 281$;
+similarly $A_2(14,6)\le \frac{.5\cdot14\cdot6}{9 - 2\cdot3\cdot.5\cdot14 + .5\cdot14\cdot6}\cdot\frac{2^{14}}{V_q(14,3)} = \frac{42}{9-42+42}\cdot\frac{2^{14}}{1+14+91+ 364} = 162$.
+
+For $w=4$,
+in the case of $A_2(13,5)$, the first denominator is less than zero, and thus we cannot apply the bound; $A_2(14,6)$ still works, however.  
+$A_2(14,6)\le \frac{.5\cdot14\cdot6}{16 - 2\cdot4\cdot.5\cdot14 + .5\cdot14\cdot6}\cdot\frac{2^{14}}{V_q(14,4)} = \frac{42}{16-56+42}\cdot\frac{2^{14}}{1+14+91+ 364+1001} = 233$.
+
+Thus the best upper bound from the Elias Bound for $A_2(13,5)=A_2(14,6)=162$.
 
@@
 
-Consequently, for our asymptotic bounds, we are interested in the largest
+For our asymptotic bounds, we are interested in the largest
 possible rate for a family of codes over $\mathbb{F}_q$ of lengths going to
@@
 
-For the rest of this section, we will consider some bounds on $A_q(n,\delta n)$
+For the rest of this section, we will consider two bounds on $A_q(n,\delta n)$
 
@@
 
-\begin{exmp}
+\subsection{Asymptotic Plotkin Bound}
+The Asymptotic Plotkin Bound gives a small improvement on the Asymptotic Single Bound.
 
-\end{exmp}
+\begin{theorem}
+Let $r=1-q$.  Then 
+\begin{equation*}
+\alpha_q(\delta)= 
+\begin{cases} 0, &\mbox r\le\delta\le1 \\ 1-\delta/r, &\mbox{} 0\le\delta < r. \end{cases}
+\end{equation*}
+\end{theorem}
 
-\subsection{Asymptotic Plotkin Bound}
+\begin{proof}[Sketch of proof]
+First, consider the case of $r\le\delta\le1$.
+Notice that we can apply the Plotkin bound directly, as $rn < \delta n = d$.
+By the Plotkin Bound, $A_q(n,\delta n) \le \frac{\delta n}{\delta n - rn}$.
+Cancelling
+out the common $n$, we get $A_q(n,\delta n) \le \frac{\delta}{\delta - r}$.  Since this value is independent of $n$, it immediately follows from the definition that $\alpha_q(\delta)=0$.
+
+Next, consider the case of $0\le\delta < r$.  Suppose that $\mathcal{C}$ is an $(n,M,\delta n)$ code where $M=A_q(n,\delta n)$ .  Our goal is to puncture $\mathcal{C}$ such that 
+we get a shorter length code $\mathcal{C}'$ with the same minimum distance as $\mathcal{C}$.
+The idea is to find a code whose $n$ is small enough that we can still apply the Plotkin bound, and then bound
+our original code $\mathcal{C}$ with the shortened code's Plotkin value.
+Use a shortening technique analgous to the one we described in lecture, as well as Section 1.5.3 of the textbook,
+let $\mathcal{C}'$ be the $(n',M',\delta n)$ code where $n' = \lfloor (\delta n -1)/ r \rfloor$ and $M' \ge M/q^{n-n'}$.  Given this code, we can show that $A_q(n,\delta n) \le q^{n-n'} \delta n$.
+Simplifying using the definition of $\alpha_q(\delta)$ completes the proof.
+\end{proof}
+
+Once again, we use MATLAB to visually compare two bounds.  This time, we consider the Asymptotic Singleton and Asymptotic Plotkin bounds.
+
+\begin{figure}[ht]
+\includegraphics[width=.8\linewidth]{asympt.png}
+\caption{Asymptotic Plotkin and Singleton bounds for $q=2$}
+\end{figure}
 
 \section{Lexicodes}
-We end our discussion on bounds with an interesting class of binary linear codes
+
+We end our discussion on bounds with an interesting class of linear codes
 called lexicodes, short for lexicographic codes.  Lexicodes are linear and meet the Gilbert bound; we will discuss the former and prove the latter.  Note that for this discussion we are 
@@
 
-We construct the lexicode $\mathcal{L}$ of length $n$ and minimum distance $d$ using a basic greedy algorithm as follows.  First, order all $n$-tuples in an array $A$ in lexicographic order:
+We construct the lexicode $\mathcal{L}(n,d)$ of length $n$ and minimum distance $d$ using a basic greedy algorithm as follows.  First, order all $n$-tuples in an array $A$ in lexicographic order:
 $A[0] = 0\cdots000$, $A[1]=0\cdots001$, $A[2]0\cdots010$, $A[3]=0\cdots011$, \ldots, $A[2^n-1] = 1\cdots111$.
@@
 
-\begin{enumerate}
+\begin{enumerate}[{\normalfont (i)}]
 \item $\mathcal{L}$ is a linear code and the vectors $\mathbf{c}_{2^i}$ are a basis of $\mathcal{L}$.  
@@
 
-Though I won't prove this, it is not difficult to see that $1.$ and $3.$ follow from $2.$    In $2.$, we are showing that all codewords in the lexicode are simply linear combinations of 
-the $c_{2^i}$ codewords, hence making the $c_{2^i}$ codewords a basis for the code.
+I claim that (i) and (iii) follow from (ii).  For (ii), we are showing that all codewords in the lexicode are simply linear combinations of 
+the $c_{2^i}$ codewords, hence making the $c_{2^i}$ codewords a basis for the code.  The sketch of the proof for (ii) involves inducting on $i$.  Essentially, the proof works
+by assuming that the second $2^{i}$ vectors in $\mathcal{L}_{i+1}$ are not necessarily generated by adding $\mathbf{c}_2^{i}$ to each of the previously chosen vectors
+in $\mathcal{L}_i$.  If you break this assumption, then you can use the notion of lexicographic order to find two vectors lexicographically ordered in a way that is not actually
+possible.
 
@@
 $\mathcal{L}$.  In general, this dimension value $k$ is not known until you have completed the construction as described above.
+
+We now consider a basic example of a lexicode $\mathcal{L}(n,d)$ and it's $\mathcal{L}_{i}$s.
 
@@
 $\mathcal{L}_4 = \mathcal{L}$. We can check to make sure that each $\mathbf{c}_j$ is a linear combination of the $\mathbf{c}_{2^i}$s. For this example, consider $\mathcal{L}_3$:
-
-Notice that this is simply the even weight vectors.  In fact, it is true that
-for any $q$.
-THIS IS THE EVEN WEIGHT CODE! prove it.
 
@@
 
-Some notable codes we have discussed in class are in fact lexicodes.
-[REFERENCE]
-
-We can prove a basic property of binary Lexicodes.  First, though, we
-need an important definition.
+It may be surprising to discover that many codes we have already discussed in lecture are in fact lexicodes.  In order to have this discussion, though, we
+first need two important definitions.
 
@@
 We have used the idea of nim-sums and zero-sums throughout the course, but instead we have
-referred to this notion in terms being even-like or odd-like.  This is the
-exact same notion, only in different terms.
+used the terms even-like or odd-like.  In the binary case, these are equivalent notions.
+
+We also need the following Lemma:
+
+\begin{lemma}
+The codewords of the lexicode $\mathcal{L}(n,d)$ are also in the lexicode $\mathcal{L}(n+1,d)$, except with an additional leading zero.
+\end{lemma}
+
+\begin{proof}
+This follows directly from how our algorithm above was constructed.  We obviously have $\mathbb{F}_q^n \subset \mathbb{F}_q^{n+1}$, and in our algorithm these will be
+the first $2^n$ vectors that are visited.  Since all that has changed is we've added a leading $0$, the algorithm will choose these same vectors $\mathcal{L}(n,d)$ vectors.
+\end{proof}
+
+In lecture, we have frequently discussed the code of all even-weight codewords.  In $\mathbb{F}_2$, this is a lexicode.
 
@@
 We will prove this by inducting on $n$.  In the base case of $n=1$,
-$\mathcal{L}=\{0\}$, which is trivially zero-sum.  Assume that for the
-lexicode of length $n$, which we will denote $\mathcal{L}(n)$, all codewords are zero-sum.  Now, we must show that all
-the codewords in $\mathcal{L}(n+1)$ are zero-sum as well.  First, note that all
-codewords in $\mathcal{L}(n)$ are also in $\mathcal{L}(n+1)$, except with an
-extra leading zero.  By our assumption, these codewords are still zero-sum, as
-adding a zero in front will not change the nim-sum calculation.
-Now, we must show that any vector we can add to this set as proscribed by our
-algorithm must necessarily be a zero-sum vector as well.
+$\mathcal{L}=\{0\}$, which is trivially zero-sum.
+
+Assume that, for the lexicode of length $n$, all codewords are zero-sum.  Now, we must show that all
+the codewords in $\mathcal{L}(n+1,2)$ are zero-sum as well.  By our lemma, all codewords in $\mathcal{L}(n,2)$ are also in $\mathcal{L}(n+1,2)$, except with an
+extra leading zero.  By our assumption, these codewords are still zero-sum, as adding a zero in front will not change the nim-sum calculation.
+
+Let ${\mathbb{F}_q^n}^*$ be the vectors of $\mathbb{F}_q^n$ with a zero appended in front of the first coordinate.
+Now, we must show that for the remaining vectors $v\in\mathbb{F}_q^{n+1} \setminus {\mathbb{F}_q^{n}}^*$that we have not yet visited, our algorithm will choose all
+even-weight vectors and none of the odd-weight vectors.
+
+First, consider the odd-weight vectors of $\mathbb{F}_q^{n+1} \setminus {\mathbb{F}_q^{n}}^*$.  Note that 
+these are actually just the even weight vectors of $\mathbb{F}_q^n$ with a $1$ appended to the front.  If you flip the first bit of each vector, you get an even weight codeword that
+we have already shown to be in $\mathcal{L}(n+1,2)$, and consequently no such odd-weight codeword can be in $\mathbb{L}(n+1,2)$.
+
+Finally, consider the even-weight vectors of $\mathbb{F}_q^{n+1} \setminus {\mathbb{F}_q^{n}}^*$.  Notice that these are just the odd-weight vectors of $\mathbb{F}_q^n$ with a $1$
+appended to the front.  By our assumption, none of the odd-weight vectors of ${\mathbb{F}_q^n}^*$ are in $\mathcal{L}(n+1,2)$.  This means that each even-weight
+vector in $\mathbb{F}_q^{n+1} \setminus {\mathbb{F}_q^{n}}^*$ will necessarily have distance $2$ from vectors in $\mathcal{L}(n,2)$ (with a zero appended to the front).  We also
+have that any two distinct even-weight vectors are at least distance $2$ from one another, as an even-weight vector can only possibly have distance one from an odd-weight vector.  
+Hence, all even-weight vectors of $\mathbb{F}_q^{n+1} \setminus {\mathbb{F}_q^{n}}^*$ will be chosen by our algorithm.
 \end{proof}
 
-For example, the binary lexicodes with $d$=3 and $n=2^m-1$ are the binary hamming codes.  It can be quite
-tedious to compute and confirm something like this by hand, so I wrote a short C++ program that implements the Lexicode algorithm as described above.
+We have also frequently discussed the Hamming codes.  In (insert reference to Greedy Codes paper), they show that the binary lexicodes with $d$=3 and $n=2^m-1$ are the Hamming codes, 
+and similarly, as one might expect considering the previous statement, the binary lexicodes with $d=4$ and $n=2^m$ are the extended Hamming codes.  We can check
+this with a simple example.
 
 \begin{exmp}
-Let $n=7$, $d=3$.  We find $\mathcal{L}= \{0000000,000111,  \}$
+Let $n=7$, $d=3$.
+It can be quite tedious to compute and confirm something like this by hand, so I wrote a short C++ program that implements the Lexicode algorithm as described above.
+We find $\mathcal{L}(7,3)$ to be $\{0,7,25,30,42,45,51,52,75,76,82,85,97,102,120,127\}$ where the binary vectors are given by their decimal representation.
 \end{exmp}
 
-Need to talk about paper
-http://ieeexplore.ieee.org/stamp/stamp.jsp?arnumber=1057187
-
-%First explore linear programming bound
-Asymptotic singleton, include 2 examples
-Asymptotic plotkin, some examples
-draw graph
-Asymptotic hamming
-	define hilbert, prove 135,136, define vq(n,a),
-	black box 2.10.3, prove 2.10.5
-
-Table of common$a_q(n,d)$ values
-Recall basic theory: thm 2.1.2, 2.1.6
-
-Sections
-
-Elias
-talk about importance
-define it
-prove two lemmas that do the heavy lifting
-easy proof to finish it off
-work out some examples
-
-Linear Programming Bound
-talk about importance
-define it
-prove it
-work out some examples
-
-Note existence of two lower bounds, say we talked about them in class
+Note that $\mathcal{L}(7,3)$ has $16$ codewords, making it a $[7,4,3]$ code.  Recall that in lecture we proved that all $[7,4,3]$ codes are the Hamming(7,4) code.
 

### 2015-04-26 asymptotic.m

@@ -1,0 +1,16 @@
+syms x;
+
+q=2;
+
+t = 0:.1:.5;
+t2 = 0:.1:1;
+r = 1-1/q;
+
+y1 = 1-t;
+y2 = 1-t/r;
+plot(t,y1,'color','r');
+hold on;
+plot(t,y2,'color','b');
+xlabel('\delta');
+ylabel('\alpha_q(\delta)');
+legend('Asymptotic Plotkin','Asymptotic Singleton');

### 2015-04-26 hamming.cpp

@@ -1,42 +1,48 @@
 #include <iostream>
 #include <cstdint>
+#include <cmath>
+#include <set>
 
 using namespace std;
 
-int popcount_1(uint64_t x);
 uint wegner(uint input);
 
-const uint64_t m1  = 0x5555555555555555; //binary: 0101...
-const uint64_t m2  = 0x3333333333333333; //binary: 00110011..
-const uint64_t m4  = 0x0f0f0f0f0f0f0f0f; //binary:  4 zeros,  4 ones ...
-const uint64_t m8  = 0x00ff00ff00ff00ff; //binary:  8 zeros,  8 ones ...
-const uint64_t m16 = 0x0000ffff0000ffff; //binary: 16 zeros, 16 ones ...
-const uint64_t m32 = 0x00000000ffffffff; //binary: 32 zeros, 32 ones
-const uint64_t hff = 0xffffffffffffffff; //binary: all ones
-const uint64_t h01 = 0x0101010101010101; //the sum of 256 to the power of 0,1,2,3...
-
-
-
 int main(){
-	uint64_t x;
-	while(1){
-		cin >> x;
-		cout << popcount_1(x) << endl;
-		cout << wegner(x) << endl;
+	
+	const int size = 7;
+	int arr[(int)pow(2,size)];
+	for (int i=0; i<pow(2,size); i++){
+		arr[i] = i;
 	}
 	
+	//base case
+	set<int> x;
+	x.insert(0);
+	
+	for (int i=1; i<pow(2,size); i++){
+	
+		set<int>::iterator it = x.begin();
+		while(it!=x.end()){
+			if (wegner(arr[i]^(*it))<3) break;
+			it++;
+		}
+		//add to x
+		if (it==x.end()){
+			x.insert(arr[i]);
+		}
+	} 
+	
+	//cout << x.size() << endl;
+	
+	set<int>::iterator it = x.begin();
+	while(it!=x.end()){
+		cout << *it << endl;
+		it++;
+	}
+	
+	cout << x.size() << endl;
+	
 	return 0;
-}
-
-
-int popcount_1(uint64_t x) {
-    x = (x & m1 ) + ((x >>  1) & m1 ); //put count of each  2 bits into those  2 bits 
-    x = (x & m2 ) + ((x >>  2) & m2 ); //put count of each  4 bits into those  4 bits 
-    x = (x & m4 ) + ((x >>  4) & m4 ); //put count of each  8 bits into those  8 bits 
[…]

### 2015-04-26 plotkin_solo.m

@@ -1,5 +1,5 @@
 syms k;
-for q = 2:5
+for q = 2:2
     r = 1-1/q;
     %data_sp_gr = zeros(100000,3);
     data_plt = zeros(100000,3);
@@ -7,7 +7,7 @@ for q = 2:5
     %count_sp = 1;
     count_plt = 1;
     
-   for n = 8:25
+   for n = 6:40
        for d=(floor(r*n)+1):n
            t = floor((d-1)/2);
            %sp = (q^n)/symsum(nchoosek(n,k)*(q-1)^k,0,t);
@@ -25,6 +25,9 @@ for q = 2:5
    
    figure;
    trisurf(tri,data_plt(1:count_plt,1),data_plt(1:count_plt,2),data_plt(1:count_plt,3));
+   xlabel('n');
+   ylabel('d');
+   zlabel('bound');
    axis vis3d
    
 %    figure;

### 2015-04-26 sphere_packing_solo.m

@@ -1,5 +1,5 @@
 syms k;
-for q = 2:5
+for q = 2:2
     r = 1-1/q;
     %data_sp_gr = zeros(100000,3);
     data_plt = zeros(100000,3);
@@ -7,7 +7,7 @@ for q = 2:5
     %count_sp = 1;
     count_plt = 1;
     
-   for n = 8:25
+   for n = 6:40
        for d=n/2:n
            t = floor((d-1)/2);
            sp = (q^n)/symsum(nchoosek(n,k)*(q-1)^k,0,t);
@@ -24,6 +24,9 @@ for q = 2:5
    
    figure;
    trisurf(tri,data_plt(1:count_plt,1),data_plt(1:count_plt,2),data_plt(1:count_plt,3));
+   xlabel('n');
+   ylabel('d');
+   zlabel('bound');
    axis vis3d
    
 %    figure;
